\begin{jobdesc}{name=sjob-alchemist}
    Items and potions specialist, able to use consumables with their full potential. Its main Stat is Water. Be an Alchemist if you want your character to be more durable, capable of staying alive longer and use items offensively better. \pc

    \textbf{Representatives}: Rikku (FFX), Chemist Job (FFV, FFT, FFTA) \pc
\end{jobdesc}

\begin{ffminipage}
{\centering \textbf{Abilities}\par }

\noindent\tability{Quick Hands}: Core Ability acquired at level 1. \taction{Draw} is a free action for you. You still need to spend initiative dice normally to use items or replace equipment. \pc

\begin{jobspec}
\crystal{fire}{12pt} & %
\tspec{Combat Medic}: Requires Fire level 3. You may equip \tequip{medium armor} and the following weapons: \tequip{Rifles / Crossbows}. \\
\crystal{water}{12pt} & %
\tspec{Impromptu Mage}: Requires Water level 3. Whenever you use an item that casts a Spell, you may use your Water Stat, rather than the Fire Stat, as Offensive Stat, to hit and deal damage. \\
\crystal{earth}{12pt} & %
\tspec{Treatment}: Requires Earth level 5. You gain access to the Quick action \taction{Treatment}. With it, you suppress bad conditions on a target, helping him to overcome his discomfort. Suppress all negative status effects on the target until the end of the round. This does not extend the status’ duration. \\
\end{jobspec}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Pharmacology}: Core Ability acquired at level 19. Whenever you use an item to recover HP or MP, double its effects. You may add your Air level to your Armor and your Water level to your Magic Armor. \pc

\begin{jobspec}
\crystal{air}{12pt} & %
\tspec{Alchemical Fire}: Requires Air level 12. Whenever you use a consumable that deals damage, the item does 10\% extra damage at the end of the round, ignoring ARM or MARM. \\
\crystal{water}{12pt} & %
\tspec{Vaccination}: Requires Water level 12. When using an item to cure status, the target becomes immune to the cured status effect for 2 rounds. \\
\crystal{fire}{12pt} & %
\tspec{Poison Distilling}: Requires Fire level 12. When using a consumable that inflicts negative status effects, the inflicted status lasts one extra round. \\
\end{jobspec}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Distribute}: Core Ability acquired at level 35. Whenever you heal someone, the amount that exceeds its maximum HP is divided evenly between you and all allies except the character that was initially cured. Distribute does not affect healing effects that target more than one target. \pc

\begin{jobspec}
\crystal{fire}{12pt} & %
\tspec{Mix}: Requires Fire level 16. You gain the Slow (1) action \taction{Mix}. You can mix two items and use them in a single action. If mixing two identical healing items, you generate the effect of the next higher-level item (for example, two \titem{Potions} turn into a \titem{Hi-Potion}). If you mix two different healing items, you generate the effect of the cheapest item in the whole Group (Mixing a \titem{Soft} and \titem{Tonic} creates the effect of Tonic in the Group). If you mix two identical battle items, you cast the next strongest Spell of the same group (two \titem{Bomb Fragment} cast the Spell \tspell{Fira}). If you mix two different battle items, you cast the Spell from the cheapest item against a Group (using the single target damage if the spell deals reduced damage to groups). Special cases may be examined individually by the GM and cause unique effects. \\
\crystal{earth}{12pt} \crystal{water}{12pt} & %
\tspec{Alchemical Tenacity}: Requires Earth and Water level 14. Increase your HP bonus by 1x your level and your MP bonus by 1x your level. \\
\end{jobspec}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Unstable Potion}: Core Ability acquired at level 50. At the beginning of each day, you can choose to sample an unstable potion, using yourself as a guinea pig. If you do, choose one of the \tstatus{Transformation} type negative statuses. You become vulnerable to it and resistant to all other \tstatus{Transformation} type statuses. Any other effects that give you resistance or immunity to the chosen status automatically fail, even from equipment. This effect lasts the entire day. \pc

\begin{jobspec}
\crystal{air}{12pt} & %
\tspec{Double Item}: Requires Air level 18. You gain the Quick action \taction{W-Item}. With it, you may use two drawn items with only one action. \\
\crystal{earth}{12pt} & %
\tspec{Auto-Potion}: Requires Earth level 18. You gain the reaction \taction{Auto-Potion}. You can use it when you suffer an attack. You draw an item from your inventory and use it on yourself. The item’s effects happen after the effects of the attack you suffered. \\
\end{jobspec}
\end{ffminipage}
