\begin{multicols}{2}

\begin{ffcolpage}
    \begin{mobstats}[name=Guard Bot, level=5, type=construct, rank=common, earth=30,air=0,fire=15,water=15, hp=55, mp=10, arm=8, marm=0]
        \mobstatrow{ \tability{Ram}: Quick \tatk{physical} action, Earth vs Air, diff 40, 12 damage (\telem{Crush})  } 
        \mobstatrow{ \tability{Block}: Reaction, Earth vs Earth, diff 40, avoids a physical attack } 
        \mobstatrow{ \tstatus{Vulnerable: Lightning}} 
    \end{mobstats} 
    These small robots serve as sentries for various laboratories and industrial facilities. Their reinforced plates make them very strong against physical blows.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Yellow Chocobo, level=6, type=beast, rank=common, earth=14,air=29,fire=20,water=18, hp=45, mp=21, arm=6, marm=4]
        \mobstatrow{ \tability{Beak}: Quick \tatk{physical} action, Air vs Air, diff 40, 6 damage (\telem{Puncture}) }
        \mobstatrow{ \tability{Dodge}: Reaction, Air vs Air, diff 70, avoids a \tatk{physical} attack}
        \mobstatrow{ \tspellblue{Choco Ball}: Blue Spell, 7 MP, Fire vs Water, diff 0, 10 damage (\telem{Crush})}
    \end{mobstats} 
    Bipedal ostrich-like birds, pony-sized, widely used as mounts. They are kind and friendly, but fierce when provoked.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Imp, level=7, type=humanoid, rank=minion, earth=18,air=32,fire=12,water=22, hp=20, mp=15, arm=2, marm=5]
        \mobstatrow{ \tability{Short Sword}: Quick \tatk{physical} action, Air vs Earth, diff 40, 6 damage (\telem{Cut}) }
        \mobstatrow{ \tspellblue{Goblin Punch}: Blue Spell, 1 MP, Air vs Earth, diff 40, 6 damage (\telem{Cut}) or instead deals 24 damage (\telem{Cut}) against 7th level targets.}
    \end{mobstats} 
    Little green humanoids, usually malignant and territorial, who form tribes. They use improvised weapons and armor. They don't have great intelligence or physical strength but are very cunning.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Venzuubius; Poison Demon, level=9, type=demon, rank=boss, earth=30,air=12,fire=40,water=19, hp=200, mp=150, arm=2, marm=2]
        \mobstatrow{ \tability{Mind Blast}: Quick \tatk{magical} action, Fire vs Water, diff 40, 12 damage (\telem{Crush}) }
        \mobstatrow{ \tability{Third Eye}: Reaction, Earth vs Earth, diff 40, blocks a melee attack }
        \mobstatrow{ \tspellblue{Flash}: Blue Spell, 14 MP, Fire vs Water, diff 0, 15 damage (\telem{Light}), if greater than diff 70, inflicts the \tstatus{Blind} status on the target until the end the round. }
        \mobstatrow{ \tspellblue{Poison Gas}: Blue Spell, 16 MP, Group, Fire vs Water, diff 70, inflicts the \tstatus{Poison} status on target until the end of next round. }
        \mobstatrow{ \tstatus{Vulnerable (Light)}, \tstatus{All Status Resist} }
    \end{mobstats} 
    One of the lesser Demon Lords, Venzuubius is arrogant and prideful. He acts with great overconfidence, treating his lesser brethren with disdain and his superiors with distrust. In battle, he tends to boast about his own abilities instead of quickly finishing his foes.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Lesser Zombie, level=12, type=undead, rank=minion, earth=50,air=12,fire=35,water=31, hp=64, mp=40, arm=13, marm=11]
        \mobstatrow{ \tability{Slam}: Quick \tatk{physical} action, Earth vs Earth, diff 40, 20 damage (\telem{Crush}) }
        \mobstatrow{ \tspell{Poison}: Black Spell, 10 MP, Fire vs Water, diff 40, 15 damage (\telem{Bio}), inflicts the \tstatus{Poison} status on target until the end of the next round. }
        \mobstatrow{ \tstatus{Zombie}, \tstatus{Vulnerable (Fire)}, \tstatus{Vulnerable (Light)}, \tstatus{Ice Immune}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Reanimated carcasses of dead humanoids who blindly follow their dark masters. They are slow and devoid of free will.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Sahuagin Captain, level=15, type=aquatic, rank=elite, earth=42,air=45,fire=41,water=31, hp=270, mp=54, arm=5, marm=15]
        \mobstatrow{ \tability{Trident}: Quick \tatk{physical} action, Air vs Air, diff 40, 12 damage (\telem{Puncture}) }
        \mobstatrow{ \tability{Aqua Rage}: Quick Ranged \tatk{magical} action, Fire vs Water, diff 40, 24 damage (\taction{Water}) }
        \mobstatrow{ \tspell{Shell}: White Spell, 14 MP, Grants Shell until the end of next round. }
        \mobstatrow{ \tspell{Cure}: White Spell, 9 MP, Fire vs Water, diff 0, Heals 20 HP\@. }
        \mobstatrow{ \tstatus{Water Resist}, \tstatus{Lightning Weakness}, \tstatus{Weaken (Speed)}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Hybrids of men and fish, Sahuagins are led into battle by dangerous captains. They are slow on land, but powerful enemies.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Risen Sorcerer, level=19, type=undead, rank=minion, earth=32,air=31,fire=86,water=55, hp=110, mp=100, arm=8, marm=15]
        \mobstatrow{ \tability{Staff}: Quick \tatk{magical} action, Fire vs Water, diff 40, 48 damage (\telem{Crush}) }
        \mobstatrow{ \tspell{Gravity}: Time Spell, 9 MP, Fire vs Water, diff 25, reduce target's HP by 25\% of its current value }
        \mobstatrow{ \tspell{Armor Up}: Time Spell, 20 MP, grants \tstatus{Strengthen (Armor)} to an ally until end of next round }
        \mobstatrow{ \tspell{Mental Up}: Time Spell, 20 MP, grants \tstatus{Strengthen (Mental)} to an ally until end of next round }
        \mobstatrow{ \tstatus{Zombie}, \tstatus{Vulnerable (Ice)}, \tstatus{Vulnerable (Light)}, \tstatus{Fire Immune}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Remains of sorcerers given will by their dark lords, these undead are notably terrifying in that they retain their intelligence and capacity for magic.  All compassion, love, and kindness are however missing.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Risen Lancer, level=19, type=undead, rank=minion, earth=65,air=60,fire=39,water=43, hp=110, mp=80, arm=15, marm=8]
        \mobstatrow{ \tability{Lance}: Quick \tatk{physical} action, Earth vs Earth, diff 40, 36 damage (\telem{Puncture}) }
        \mobstatrow{ \tability{Wide Arc}: Slow (4) \tatk{physical} action, Earth vs Earth, diff 40, 36 damage. Another random enemy suffers 25\% of the damage dealt, ignoring ARM }
        \mobstatrow{ \tstatus{Zombie}, \tstatus{Vulnerable (Ice)}, \tstatus{Vulnerable (Light)}, \tstatus{Fire Immune}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Corpses of great lancers from the past, these undead are given will by their dark lords and are notably powerful in that they can match the living in cunning.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=False Priest, level=20, type=humanoid, rank=elite, earth=30,air=43,fire=75,water=72, hp=500, mp=200, arm=8, marm=20]
        \mobstatrow{ \tability{Wand}: Ranged Quick \tatk{magical} action, Fire vs Fire, diff 40, 42 damage (\telem{Crush}) }
        \mobstatrow{ \tspell{Blind}: Black Spell, Fire vs Water, diff 70, inflicts the \tstatus{Blind} status until the end of next round }
        \mobstatrow{ \tspell{Fire Wave}: Spell, 16 MP, Fire vs Water, diff 0, 49 single damage (\telem{Fire}) or 35 group damage (\telem{Fire}) }
        \mobstatrow{ \tspell{Summon Risen}: Spell, 20 MP, Summon two random Risen minions.  This may be used only if the False Priest has no allies. }
        \mobstatrow{ \tstatus{Vulnerable (Ice)}, \tstatus{Vulnerable (Lightning)}, \tstatus{Shadow Immune}, \tstatus{Immune: Death}, \tstatus{Immune: Stone}, \tstatus{Immune: Gravity} }
    \end{mobstats} 
    This evil priest command Risen skeletons. He may summon them do his biddings, using nearby corpses. However, his powers can't raise undead armies\ldots{}\ yet.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Giant Bat, level=21, type=beast, rank=minion, earth=60,air=69,fire=60,water=30, hp=116, mp=112, arm=32, marm=21]
        \mobstatrow{ \tability{Bite}: Quick \tatk{physical} action, Earth vs Air, diff 40, 36 damage (\telem{Cut}) }
        \mobstatrow{ \tability{Arrow Guard}: Reaction, Air vs Air, diff 30, avoids a Ranged \tatk{physical} attack }
        \mobstatrow{ \tspellblue{Red Feast}: Blue Spell, 10 MP, Earth vs Air, diff 40, 30 damage (\telem{Puncture}), The Giant Bat heals itself half of the damage dealt. }
        \mobstatrow{ \tstatus{Flight}, \tstatus{Vulnerable (Air)}, \tstatus{Immune: Blind}, \tstatus{Improved Critical} }
    \end{mobstats} 
    Huge blood-sucker bats who live in caverns. They hate sunlight. Usually they don't attack adventurers unless they're provoked, or someone trespasses their lair.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Red Flan, level=22, type=abberation, rank=common, earth=51,air=48,fire=75,water=65, hp=255, mp=148, arm=20, marm=26]
        \mobstatrow{ \tability{Slam}: Quick \tatk{physical} action, Earth vs Earth, diff 40, 25 damage (\telem{Crush}) }
        \mobstatrow{ \tspell{Fire}: Black Spell, 8 MP, Fire vs Water, diff 0, 35 damage (\telem{Fire}) }
        \mobstatrow{ \tspell{Flame}: Spell, 15 MP, Group, Fire vs Water, diff 0, 25 group damage (\telem{Fire}) }
        \mobstatrow{ \tstatus{Resist (Cut)}, \tstatus{Resist (Crush)}, \tstatus{Resist (Puncture)}, \tstatus{Fire Absorb}, \tstatus{Vulnerable (Ice)}, \tstatus{Vulnerable (Water)}, \tstatus{Immune: Weaken} }
    \end{mobstats} 
    Amorphous elemental that looks like goo and have dominion over fire. Common in volcanic areas. They are hot to the touch and very aggressive.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Iron Golem, level=30, type=construct, rank=common, earth=112,air=34,fire=82,water=96, hp=400, mp=255, arm=70, marm=30]
        \mobstatrow{ \tability{Axe}: Slow (1) \tatk{physical} action, Earth vs Air, diff 40, 110 damage (\telem{Cut}) }
        \mobstatrow{ \tability{Block}: Reaction, Earth vs Earth, diff 40, avoid a \tatk{physical} attack. }
        \mobstatrow{ \tspellblue{Matra Magic}: Blue Spell, 55 MP, Group, Fire vs Water, diff 0, 80 group damage (\telem{Fire}) }
        \mobstatrow{ \tability{Rust Spray}: Quick Ranged \tatk{magical} action, Group, Fire vs Water, diff 70, inflicts the \tstatus{Weaken (Armor)} status until the end of next round }
        \mobstatrow{ \tstatus{Immune: Virus}, \tstatus{Vulnerable (Lightning)}, \tstatus{Immune (Cut)}, \tstatus{Immune: Mental}, \tstatus{Immune: Toxic}, \tstatus{Immune: Transform}, \tstatus{Immune: Death} }
    \end{mobstats} 
    A huge construct animated by magic, wielding a rusty axe. They have no free will, limited to comply with its creator’s orders.\pw%
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Kraken, level=38, type=aquatic, rank=elite, earth=99,air=84,fire=91,water=123, hp=1500, mp=555, arm=43, marm=95]
        \mobstatrow{ \tability{Tentacle}: Quick \tatk{physical} action, Earth vs Air, diff 40, 90 damage (\telem{Crush}) }
        \mobstatrow{ \tspellblue{Aqua Rake}: Blue Magic, 85 MP, Group, Fire vs Water, diff 0, 117 damage (\telem{Water}) }
        \mobstatrow{ \tability{Ink}: Quick \tatk{magical} action, Group, Fire vs Water, diff 70, inflicts the \tstatus{Blind} status on this and the next two rounds }
        \mobstatrow{ \tability{Devour}: Slow (2) \tatk{physical} action, Earth vs Earth, diff 80, Inflicts the \tstatus{Condemn} status until the end of next round }
        \mobstatrow{ \tstatus{Immune (Water)}, \tstatus{Vulnerable (Lightning)}, \tstatus{Immune: Fatal}, \tstatus{Immune: Blind}, \tstatus{Vulnerable: Mental} }
    \end{mobstats} 
    An octopus and squid hybrid, the Kraken is a colossal beast that terrorizes the oceans, destroying ships with its powerful tentacles.\pw%
\end{ffcolpage}

\end{multicols}