\label{ch:inventory}

\begin{multicols}{2}
\section{Wealth}
\label{sec:inv-wealth}
Gil is the currency present in most Final Fantasy games. Depending on how technologically advanced the world is, it can take many forms: gold coins, paper money, checks, planetary credit\ldots{} Regardless of Gil’s actual format, it will be an abstraction for monetary values.

Gil is a character reward as important as experience. Many Jobs take into account not only the Stat levels, but also the character’s equipment and items to measure their power. Depriving an \nameref{subsec:pjob-archer}, for example, of a suitable weapon can make the character feel extremely weak in comparison to a Mage. Imagine an \nameref{subsec:sjob-alchemist} who don’t even have an item to use? Gil is such an important reward that there is a Job dedicated to it: the \nameref{subsec:pjob-rogue}.

\subsection{Mundane Items}
\label{subsec:inv-mundane}
How much does a mundane item cost? How many feet of rope, how many torches, how many sleeping bags a character has or may possess? The answer has to do directly with the economy of a Final Fantasy world: \textbf{mundane items are free}.

Everything that costs Gil refers to combat. All other items should be designed according to the context and the Challenges and Destiny system, starting at page \pageref{ch:engine}. Mundane items are a tool for the Game Master to use in drama; they were never important in any game in the series, unless the situation said so. If you decide that your character should have a torch, they will. If it is important that your character does not have a torch, they will not. If you are unsure, use a Challenge. Maybe the Bottomless Pockets Quirk may help.

This does not mean that the characters have access to everything. For example: an aircraft is not combat-related and therefore is a "mundane item" is not available to the characters unless the Game Master decides so. Players can’t simply demand to own something simply because the item is mundane and therefore "free" as in our example aircraft. Use that desire to create an adventure - or a small campaign arc, perhaps - and then give them the aircraft. Use the acquisition of the aircraft to support the history and not as an accounting exercise.

That's the spirit of mundane items: something that helps you tell a story, not an exercise to prepare the best shopping list. Nothing prevents, however, NPCs to pay big bucks for a mundane item. In fact, some wealthy patrons might be willing to pay good sums of Gil for a frame, or a jewel or a miniaturized reactor that have no value for player characters. Go figure!

\subsection{Acquiring Gil}
\label{subsec:inv-acquire}
\end{multicols}