\begin{multicols}{2}
\section{Quirks}
Quirks are characteristics that define your
character's personality and/or backstory. They
give the player some tips on how to roleplay their
character and are a tool both to earn Destiny
Points and to use them. Some Quirk also got a
keyword. You may not have more than one quirk
with the same keyword, so you can't be Caustic
and Empathic at the same time. And absolutely no
Half-Viera/Half-Elvaan, please!

Destiny Points are a shared group resource
that may be used to give the players some control
in the narrative. They may be used to turn a failed
Challenge into a successful one, to give tips and
directions, to perform heroic actions that surpass
human capacity and even to cheat death, among
various other uses. Details on how to earn and how
to spend Destiny Points are on the Game Engine
Chapter, starting at page 13.

\subsection{Quirk List}

\textbf{Arrogant}: You don’t back off from
challenges and don’t submit to the will of others.
You may spend Destiny Points to resist
intimidation. However, you do not take insults
lightly and don’t refuse challenges. Earn Destiny
Points when this attitude causes you problems.

\textbf{Bangaa (racial)}: A people of biped
lizard men. They are as tall as humans,
but significantly stronger and
covered with hard scales. You may use
Destiny Points due to your great strength,
leathery skin and high strength to overcome physical
Challenges.
However, your race has a terrible vision and it is
not uncommon for Bangaa to cover their eyes to
focus only on hearing and smell. Although you can
still see, but the lack of an accurate vision may
cause you problems, and if that happens, earn
Destiny Points.

\textbf{Bottomless Pockets}: You usually have
everything always at hand. Spend Destiny Points to
find things you did not expect, as that wrench you
were just looking for! However, sometimes you
simply won’t find something you were sure that
were with you. When this causes you problems,
earn Destiny Points.

\textbf{Brute (body)}: You are very strong and
heavy. Spend Destiny Points to overcome
challenges whenever your muscle power really
makes a difference. However, your weight and lack
of reflexes can cause you problems, granting you
Destiny Points.

\textbf{Caustic (charisma)}: You attract dislike
and people feel uncomfortable by your side. You
may use Destiny Points to intimidate or otherwise
impose your will on others. You receive Destiny
Points when this lack of sympathy causes you
problems.

\textbf{Contacts}: You have contacts to obtain
information or favors. Decide at character creation
what kind of contacts you have and what kind of
favors they would be willing to do. To use these
favors, spend Destiny Points. However, your
contacts may ask dangerous favors or cause you
problems, granting you Destiny points.

\textbf{Compulsive Liar (honesty)}: For some
reason, telling the truth is very hard for you. Worse,
others believe! Use Destiny Points to make people
believe your lies, especially the most ridiculous,
and earn Destiny Points whenever your lack of
honesty causes you problems.

\textbf{Dwarf (racial)}:
Creatures that live underground in caves and
mines, building great kingdoms and castles
under the rock. They are generally smaller
and more muscular than humans, possessing an
innate aptitude for metallurgy and technology.
You may use Destiny Points in situations involving
explosives, machinery and mining, activities for
which dwarves are renowned. However, the time
spent in the darkness turns sunlight into an
ongoing discomfort, making you feel bad in bright
light. Whenever this causes you problems, earn
Destiny Points.

\textbf{Elvaan (racial)}: Proud, athletic, slender and
towering, Elvaan are known for their prominent pointed
ears, often stretching ten to fifteen centimeters to the
sides of their heads. Some call them the Elves or Elezen.
You may use Destiny Points in situations that require
courage, confidence and willpower. However, Elvaan
are famous for their arrogance and inability to
forgive offenses, whether real or imagined.
Whenever this causes you problems, earn Destiny
Points.

\textbf{Empathic (charisma)}: You attract
sympathy and people feel comfortable at your side.
You may use Destiny Points to attract sympathy
and good impressions. However, people tend to
not take you seriously. If this causes you problems,
earn Destiny Points.

\textbf{Fast (body)}: You are fast and light. Spend
Destiny Points to use your speed to your
advantage but earn Destiny Points when your lack
of strength or resistance causes you problems.

\textbf{Feral (animal)}: You were raised by beasts,
monsters or a savage tribe. You relate well with
animals. Use Destiny Points to attract animal
sympathy and calm them. However, you are unable
to get along with other humans and earn Destiny
Points whenever that causes you problems.

\textbf{Focused}: You are focused on some issues
(decide which). Unfortunately, this leaves you with
little regard for other subjects. You may use
Destiny Points to remember specific knowledge of
your studies. Earn Destiny Points when your lack
of attention to other matters causes you problems.

\textbf{Intuitive Magic – Elemental}: You can
spend Destiny Points to manipulate fire, lightning
and ice, creating small magical effects. Your
magical skills, however, can’t be used in combat.
Sometimes, magic does not work the way or when
you want, and if this causes you problems, earn
Destiny Points.

\textbf{Intuitive Magic – Forces}: You can spend
Destiny Points to telekinetically manipulate
objects, as well as air, earth and water, performing
small magical effects. Your magical skills, however,
can’t be used in combat. Sometimes, magic does
not work the way or when you want, and if this
causes you problems, earn Destiny Points.

\textbf{Intuitive Magic – Illusion}: You can spend
Destiny Points to manipulate lights, shadows and
illusions, performing small magical effects. Your
magical skills, however, can’t be used in combat.
Sometimes, magic does not work the way or when
you want, and if this causes you problems, earn
Destiny Points.

\textbf{Lalafell (racial)}: These little creatures are
among the smallest known races, hardly
reaching more than a meter tall. In their own
language, they call themselves Tarutaru.
You may spend Destiny Points to make
small magical effects by manipulating
telekinetically objects as well as to control
light and shadows. Their magical skills, however,
can’t be used in combat. 
Their small stature and lack of physical strength
can cause problems when they try to overcome
situations that require strength and endurance.
Whenever this happens, earn Destiny Points.

\textbf{Lycanthrope}: Your senses are much more
acute than usual. You can use Destiny Points to
track by scent or discover things that only your
keen senses would find. But his bestial blood tries
to take control of you, and you have a constant
internal struggle to not act like an animal.
Whenever this cause problems, earn Destiny
Points.

\textbf{Moogle (racial)}: Their
appearance is similar to a
humanoid cat, usually white in
color, with small wings of red or
purple color and an antenna on
his head ending in a red ball
(pompom). Their ears are like
those of a cat or a dog. Despite
having wings, they can't fly, but
their pompoms give almost telepathic abilities
with other moogle, building what some scholars
call Mognet. You may spend Destiny Points to
gather information or send messages through
Mognet to other moogle. However, their spoken
language heavily depends on the kupo word,
which can have several meanings depending on
the intonation and body movements. Because of
this, communication with other races is full of
misunderstandings. Whenever this causes you
problems, earn Destiny Points.

\textbf{Naive Idealist}: You see life through the
lens of a personal code of conduct, or some
religious fanaticism, or an ideological utopia.
Either way, you're very attached to that ideals, and
you can draw strength from them. The details of
your ideal code must be fleshed out with the GM,
but you can spend Destiny points to face incredible
odds when adhering to it. However, you're gullible
and easily manipulable, as your ideals may be used
to cause you problems, earning you Destiny Points.

\textbf{Natural Hunter (animal)}: You feel more
comfortable away from civilization. Forests are
your second home. You can use Destiny Points to
hunt, seek shelter and track in natural
environments. However, you are already so used to
kill animals that they avoid you and feel
uncomfortable around you. If this causes you
problems, earn Destiny points.

\textbf{Nu Mou (racial)}: They have similarities
with dogs, with elongated snouts, furry tails and
big, floppy, ears. Their
short stature, around a
meter and a half tall, and
their tendency to a
stooped posture, cause
them to be very small.
They have a fragile
constitution, but they are
very intelligent and tend to live three times more
than normal humans. You may use Destiny Points
in situations involving patience, common sense
and obscure knowledge, especially magical
knowledge. They are also slow and not very
athletic. Whenever this causes you problems, earn
Destiny Points.

\textbf{Paranoid}: You're always aware of the
dangers that can arise at any time. Spend Destiny
Points to perceive things that only your keen
senses may notice. However, you suspect everyone
and everything, and if this causes you problems,
earn Destiny Points.

\textbf{Roegadyn (racial)}: Also known as Galka,
this race with slightly
ursine appearance has
huge bodies, often over
two meters tall. Despite
their great strength and
power, they are renowned
for self-knowledge and
phlegm. You may use
Destiny Points in
situations involving self-
control and great physical
strength. But often their
overly calm attitude may look like apathy or
simply laziness. Whenever this causes you
problems, earn Destiny Points.

\textbf{Straight Arrow (honesty)}: You're a
straight arrow, rarely lie and got a reputation for
honesty. You may spend Destiny Points to make
people believe and trust you. Earn Destiny points
whenever your honesty causes you problems.

\textbf{Uncommon Beauty}: You are very
beautiful and can use your beauty to attract
attention and get good impressions. You may use
Destiny Points to influence other characters who
would feel attracted to you. Whenever your beauty
causes you problems, earn Destiny Points.

\textbf{Viera (racial)}:
The Viera have two sub-races. The most common
live in temperate forests
and has long rabbit ears,
but there is a sub-race that
lives in tropical jungles
and has feline characteristics rather than
rabbit’s. This sub-breed is
commonly called Mithra
or Miqo'te. Regardless of
the sub-race, they are
mostly female, with males
being only about twenty percent of the population.
Moreover, they are closely linked to the forests and
jungles where they live. You may use Destiny
Points to communicate with trees, although their
cognitive ability is very limited. On the other hand,
you feel extremely uncomfortable in urban
environments, and can even become ill if you stay
away from the natural environment for a long time.
Whenever this causes you problems, earn Destiny
Points.

\textbf{Visions}: For some reason, you have visions
that can give you tips of the future or just torture
you. Spend Destiny Points for good visions and
earn Destiny Points when flashbacks cause you
trouble.

You may also want to create your own
Quirks. Choose a trait that defines your character
and talk with your GM to turn into a Quirk.
However, there are three guidelines that should
be followed. First, a Quirk must be able to
provide the player ways to spend Destiny Points
to overcome Challenges; second, a quirk must be
able to provide the GM ways to create problems
for the group; and lastly, a quirk may not
influence tactical combat rolls.

\section{Stats and Skills}
\subsection{Stats}
Characters have four Stats, each connected
to a crystal - Earth, Air, Fire and Water. Each Stat
has a value and levels. For every 10 points in its
value, the Stat earns another level. Stat's value
varies from 0 to 255 and, consequently, between 0
and 25 levels. The sum of a character’s Stat levels
is his Character level.

For example, a 30th level character may
have Earth 52 (5th level), Air 108 (10th level), Fire
80 (8th level) and Water 75 (7th level). Each Stat
has 6 skills associated to it. The sum of all Skill
levels a character has in all skills linked to a
particular Stat may not be higher than its Stat level.
Thus, the above character has 10 points to spend
in all skills but may not spend more than 5 points
in Earth skills, no more than 8 points in Fire skills
and no more than 7 points in Water Skills.

Stats are also used in the tactical combat
system. Each roll in combat uses one Offensive
and one Defensive Stat. Earth is usually the
Offensive Stat for attacks that depends on the
user's brute force and physicality and is the
Defensive Stat to attacks that may be prevented by
the defender's physical strength, health and
muscle power.

Attacks that rely on the user's speed,
finesse and skill use Air as its Offensive Stat. It is
the Defensive Stat against attacks that may be
evaded by the defender's reflexes and agility. A
primarily Offensive Stat, Fire is used in attacks
that rely on the user's intelligence and magical
ability. If an attack may be avoided by the
defender's insight, it uses Fire as it Defensive Stat.

Lastly, attacks that depends on the user's
charisma and willpower to hit uses Water as its
Offensive Stat. However, it is a mainly Defensive
Stat, as attacks that may be resisted by the user's
mental strength and magical defenses should use
it. Besides its offense and defense implications,
players should note that your Earth Value is added
to your hit points (HP) and your Water Value is
added to your magic points (MP) value.

Stats are increased using experience
points. The cost to increase a Stat's value by a
single point is one plus twice the Stat level. Thus, a
Stat costs 1 experience point per Stat point while
at level 0 (value from 0 to 9); 3 experience points
per Stat point while at level 1 (value 10 to 19); 5
XP per Stat point while at level 2 (value 20 to 29);
and so on. Starting on page 125, there is a table
with the total XP cost for each Stat value.

\subsection{Skills}
Skills are tools that the characters have to
overcome Challenges. Each Challenge must relate
to a Skill. Each Skill level means the player may re-
roll once a Challenge related to that Skill. For
example, a character with 3 levels in Strength Skill
can re-roll the d100 3 times to overcome Strength
Challenges.

Earth Skills involve brute strength,
toughness, physical prowess and bulk. A
character's Earth level is his limit to spend
points in Strength, Climbing, Swimming,
Intimidation, Tolerance or Jumping.

Air Skills involve movement, finesse and
body coordination. A character's Air level is
his limit to spend points in Running, Stealth,
Piloting, Riding, Thievery or Acrobatics.

Fire Skills involve intelligence, knowledge
and wisdom. A character's Fire level is his
limit to spend points in Infiltration,
Perception, Medicine, Survival, Technology
or Wisdom.

Water Skills involve willpower and
charisma. A character's Water level is his
limit to spend points in Willpower, Bluff,
Handle Animal, Charisma, Performance or
Magic.

Below is a description of each Skill and
examples of Challenges associated with them.

\textbf{Acrobatics (Air)}: Ability to perform
acrobatic maneuvers and maintain balance in
difficult situations. Can be used in situations
where the character may lose balance, must walk
on cliffs or wires, or in situations where it hangs
on masts, chandeliers or ropes.

\textbf{Bluff (Water)}: Ability to lie, cheat, conceal
and seduce. It can be used in situations to deceive,
pretend, or otherwise attempt to conceive your
true intentions.

\textbf{Charisma (Water)}: Personal magnetism
and ability to impress. It can be used in situations
involving the reactions of non-player characters,
sometimes even without any specific action by the
character.

\textbf{Climbing (Earth)}: Climbing speed and
technique. It can be used in situations that involve
climbing walls, mountains, trees and other
obstacles.

\textbf{Handle Animal (Water)}: Ability to soothe
and train animals and monsters. It can be used in
situations requiring empathy with animals, to
calm wildlife, train animals or prevent them from
attacking someone.

\textbf{Infiltration (Fire)}: Ability to open locks
and gain access to locked locations. It can include
both the ability to unlock locks with lock picks as
the ability to fake access cards in more modern
environments.

\textbf{Intimidation (Earth)}: Ability to impose
your will through coercion, threats and power
displays. It can be used in situations where the
character wants to impose its will in the most
direct way possible.

\textbf{Jumping (Earth)}: Jumping capacity,
involving both the distance as the height. It can be
used in situations involving the ability to
overcome pits or to reach high platforms.

\textbf{Magic (Water)}: Knowledge of arcane
magic. It can be used in situations involving
knowledge of the magical forces of the world and
its mysteries.

\textbf{Medicine (Fire)}: Knowledge of anatomy,
healing, herbal medicines and medical techniques.
It can be used in various situations involving
diseases, poisonings and remedies.

\textbf{Perception (Fire)}:
Ability to distinguish detail
with the five senses. It can be
used in situations involving
sight, hearing, smell, touch or
taste.

\textbf{Performance (Water)}:
Ability to act, sing,
dance or perform other
forms of art. It can be carried
out in situations involving
artistic performances, such
as an opera.

\textbf{Piloting (Air)}: Ability to drive inanimate
machines, ranging from chariots and carriages to
giant robots and aircraft, depending on the
setting’s technology.

\textbf{Riding (Air)}: Ability to ride animals such
as chocobos. It can be used in situations involving
the ability to ride animals, in pursuits or to do
mounted maneuvers.

\textbf{Running (Air)}: Ability to walk and run fast
and for long distances. It can be used in situations
involving the running speed and endurance in long
distance runs.

\textbf{Stealth (Air)}: Ability to hide and move
silently. It can be used in situations when the
character doesn’t want to be noticed.

\textbf{Strength (Earth)}: Strength and physical
ability. It can be used in situations involving the
character's ability to lift, pull, push and knock
down things.

\textbf{Survival (Fire)}: Ability to relate to the
natural world and get food, water and shelter
outdoors. It can be used in situations where the
character needs to hunt and gather food and water
in wild environments.

\textbf{Swimming (Earth)}: Ability to cross
distances by swimming. It can be used in
situations involving the need to cross rivers, lakes,
seas or simply to avoid drowning.

\textbf{Technology (Fire)}: Ability to relate to
existing technology on the world, varying
according to the setting’s technology level. It can
vary from gear-operated primitive machines to the
operation and maintenance of sophisticated
computers.

\textbf{Thievery (Air)}: Ability to perform hands
tricks, as making small objects exchange owner
without anyone noticing. It can be used in
situations involving theft, traps or sleight of hand.

\textbf{Tolerance (Earth)}: Ability to resist hot
and cold environments, hunger, thirst, drowning
and suffocation. It can be used in situations where
the character must overcome physical hardships.

\textbf{Willpower (Water)}: Ability to resist
intimidation, pain, suffering and torture. It can be
used to withstand suffering and to endure the
physical and emotional hardships.

\textbf{Wisdom (Fire)}: Common sense and the
ability to distinguish illusions, tricks and
deceptions. It can be used in situations that
require the character’s judgment to avoid being
fooled.
\end{multicols}