\begin{jobdesc}[name=sjob-defender]
    With cover and protective maneuvers, a Defender seeks to protect its allies against attacks, often placing himself in danger. Its main Stat is Earth. Be a Defender if you want to protect your allies, shielding them from damage or negative status effects. \pc%

    \textbf{Representatives}: Cecil Harvey (FFIV), Paladin Job (FFXI, FFTA) \pc%
\end{jobdesc}

\begin{tabjob}
    \multicolumn{2}{p{\textwidth}}{\tability{Cover}: Core Ability acquired at level 1. You gain the \actype{reaction=true} \taction{Cover}. Use it when an ally is hit by a physical attack. You are hit by the attack, rather than the ally. As a free action, you can use another reaction against the attack, if able.} \\
    \tabjobspec{}
    \crystal{earth}{12pt} & %
    \tspec{Sentinel}: Requires Earth level 5. As a free action, when an ally with current HP equal to or less than 25\% or his max HP suffers a physical attack, you may suffer the attack instead of the original target. \\
    \crystal{water}{12pt} & %
    \tspec{Arcane Defense}: Requires Water level 4. You may use \taction{Cover} to react when an ally suffers a magical attack or Spell. Your \taction{Shared Pain} reaction can also be used when you suffer a Melee magical attack. \\
    \crystal{earth}{12pt} \crystal{air}{12pt} & %
    \tspec{Armor Training}: Requires Earth and Air level 3. Use the greater between Earth and Air Values to calculate your HP\@. Also, increase your HP bonus multiplier by one at all levels, if its level 1 value is 4x or lower, and gain one armor type as a equipment choice. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Share the Pain}: Core Ability acquired at level 19. You may add your Air level to your ARM and your Fire level to your MARM. You gain the \actype{reaction=true} \taction{Shared Pain}. Use when hit by a Melee physical attack. Do an Earth vs Earth attack, difficulty 40. If successful, split the HP lost evenly between you and the opponent who attacked you. If you roll a critical hit, the enemy loses HP instead of you\@. } \\
    \tabjobspec{}
    \crystal{fire}{12pt} \crystal{water}{12pt} & %
    \tspec{Healing Wind}: Requires Fire and Water level 5. Increase your MP bonus multiplier by one. In addition, you gain the \tspellgroup{Healing} Spell group. Your \tspellgroup{Healing}-group Spells cost double MP and target you and all your allies rather than a single target (using single-target healing value for you and each ally). \\
    \crystal{earth}{12pt} \crystal{air}{12pt} \crystal{fire}{12pt} & %
    \tspec{Defensive Mastery}: Requires Earth, Air and Fire level 8. Reduce by 20 the difficulty of any reaction you perform. \\
    \crystal{earth}{12pt}& %
    \tspec{Noble Sacrifice}: Requires Earth level 9. As a free action, when an ally suffers an attack that inflicts a negative status effect you don't have, you may suffer its effects instead. When using \tspec{Noble Sacrifice}, ignore your immunities. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Astra}: Core Ability acquired at level 35. You gain the \tspell{Astra} Spell.} \\
    \tabjobspec{}
    \crystal{earth}{12pt} \crystal{fire}{12pt} & %
    \tspec{Astraga}: Requires Earth and Fire level 13. You gain the \tspell{Astraga} Spell. \\
    \crystal{air}{12pt} \crystal{water}{12pt} & %
    \tspec{Perseus's Mirror}: Requires Air and Water level 13. Whenever a status effect caused by an opponent is blocked by the \tspell{Astra} Spell, you may immediately repeat the blocked attack as an interrupt using that opponent as target. When you sucessfully hit with the \taction{Shared Pain} reaction, you also inflict all status effects caused to you by the enemy's attack. If you critical hit with \taction{Shared Pain}, you do not suffer the status effect and still inflict it on the enemy. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Immortal Body}: Core Ability acquired at level 50. At the start of each combat, you gain the \tstatus{Reraise} status.} \\
    \tabjobspec{}
    \crystal{water}{12pt} & %
    \tspec{Immortal Soul}: Requires Water level 16. You gain the \tspell{Great Gospel} Spell. \\
    \crystal{air}{12pt} & %
    \tspec{Immortal Technique}: Requires Air level 16. Choose a reaction from any Job. You gain that reaction. \\
\end{tabjob}