\begin{jobdesc}[name=sjob-dervish]
    Offensive Job focused on fighting with two weapons to strike fast and often. Its main Stat is Air. Be a Dervish if you want to increase the amount and speed of your actions and be a great physical damage dealer. \pc%

    \textbf{Representatives}: Edward Geraldine “Edge” Eblan (FFIV), Clyde “Shadow” Arrowny (FFVI), Ninja Job (FFI, FFIII, FFV, FFXI, FFT, FFTA) \pc%
\end{jobdesc}

\begin{tabjob}
    \multicolumn{2}{p{\textwidth}}{\tability{Ambidexterity}: Core Ability acquired at level 1. You may equip Twin Blades.} \\
    \tabjobspec{}
    \crystal{air}{12pt} & %
    \tspec{Quick Draw}: Requires level Air 3. Once per round as a free action, you can switch weapons as if you had used \taction{Item}. \\
    \crystal{level}{12pt} & %
    \tspec{Killer's Garments}: Requires level 1. You may equip \tequip{medium armor}, \tequip{Bows}, and \tequip{Throwing Weapons}. \\
    \crystal{air}{12pt} \crystal{fire}{12pt} & %
    \tspec{Deadly Dance}: Requires Air level 5 and Fire level 4. Whenever you hit the \taction{Attack} action, you may lower the value of one of your initiative dice by 1, to a minimum of the current phase. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Critical Speed}: Core Ability acquired at level 19. You may add your Air level to your ARM and your Fire level to your MARM\@. While your current HP is 25\% of your max HP or less, you gain the \tstatus{Haste} status. You lose this status if your current HP is more than 25\% of your max HP for any reason.} \\
    \tabjobspec{}
    \crystal{earth}{12pt} \crystal{water}{12pt} & %
    \tspec{Zen Focus}: Requires Earth and Water level 7. At the beginning of each round, you may roll one fewer initiative dice to gain one extra die in a phase you have no initiative dice (you choose which phase after all enemies have rolled initiative). \\
    \crystal{air}{12pt} \crystal{fire}{12pt} & %
    \tspec{Danger Zone}: Requires Air and Fire level 6. At the beginning of each round, you may spend HP equal to 25\% of your max HP to receive the \tstatus{Haste} status during this round. \\
    \crystal{fire}{12pt} \crystal{water}{12pt} & %
    \tspec{Two-Weapon Defense}: Requires Fire level 9 and Water level 5. You gain the reaction \taction{Double Parry}. Use when hit by a Melee \tatk{physical} attack. Do an (the greater of Air or Earth) vs Earth attack, difficulty 40. If successful, you ignore the attack’s effects. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Deadly Accuracy}: Core Ability acquired at level 35. Once per action, after rolling an attack, you may reduce or increase the d100 result by 1.} \\
    \tabjobspec{}
    \crystal{air}{12pt} & %
    \tspec{Deep Cut}: Requires Air level 15. When you attain a critical hit with an action that deals damage, ignore the target’s ARM and MARM\@. \\
    \crystal{water}{12pt} & %
    \tspec{Lethal Precision}: Requires Water level 16. If you discard an initiative dice after rolling an attack that may not have critical hits, you deal double damage in case of a critical hit. This ability may not be used with Spells. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Fierce Assault}: Core Ability acquired at level 50. After you deal physical damage to a target, your subsequent physical attacks against that target in this phase ignore Armor. After you deal magical damage to a target, your subsequent magical attacks against that target in this phase ignore Magic Armor.} \\
    \tabjobspec{}
    \crystal{earth}{12pt} & %
    \tspec{Rain of Blows}: Requires level 16 in Earth. Once per round, after making a successful \taction{Attack}, you may repeat the action as a free action. \\
    \crystal{fire}{12pt} & %
    \tspec{Precise Hits}: Requires Fire level 16. Once per round, you may re-roll an attack when using a \tatk{physical} or \tatk{magical} action. \\
\end{tabjob}