\label{subsec:sjob-runeknight}
\begin{jobdesc}[name=sjob-runeknight]
    This Job is focused on neutralizing mages, able to prevent the casting of spells and avoiding its effects. Its main Stat is Fire. Be a Rune Knight if you want to protect yourself from harmful magic effects and have the tools to overcome enemies whose power comes from magical abilities. \pc

    \textbf{Representatives}: Celes Chere (FFVI) Dycedarg Beoulve (FFT), Zalbaag Beoulve (FFT) \pc
\end{jobdesc}

\begin{ffminipage}
{\centering \textbf{Abilities}\par }

\noindent\tability{Defensive Runes}: Ability acquired Base at level 1. You may equip \tequip{light armor} and gain the reaction \taction{Runic}. Use it when hit by a Spell or a \tatk{magical} attack. Perform a Fire vs Fire attack, difficulty 40. If successful, the attack or Spell has no effect. \pc

\begin{jobchoice}
\crystal{water}{12pt} & %
\tspec{Magic Drain}: Requires Water level 4. If you succeed with \taction{Runic}, recover the same amount of MP spent by the opponent. \\
\crystal{fire}{12pt} & %
\tspec{Runic Area}: Requires Fire level 5. Your \taction{Runic} reaction may also be used when a Spell or \tatk{magical} attack hits an ally. \\
\crystal{air}{12pt} & %
\tspec{Offensive Runes}: Requires Air level 4. Your \taction{Runic} reaction may also be used when a Spell or \tatk{magical} attack hits an opponent. \\
\crystal{earth}{12pt} & %
\tspec{Exotic Runes}: Requires Earth level 3. When using your \taction{Runic} reaction, you may swap the Offensive Stat to Air or Water. If you do, reduce the reaction's difficulty by 10. \\
\end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Spell Protection}: Core Ability acquired at level 19. You may add your Air level to your ARM and your Fire level to your MARM. While your current HP is 25\% of your max HP or less, you gain the \tstatus{Shell} status. You lose this status if your current HP is more than 25\% of your max HP for any reason. \pc

\begin{jobchoice}
\crystal{earth}{12pt} & %
\tspec{Protection Circle}: Requires Earth level 12. While your current HP is 25\% of your max HP or less, your allies gain the \tstatus{Shell} status. Your allies lose this status if your current HP is more than 25\% of your max HP for any reason. \\
\crystal{water}{12pt} & %
\tspec{Enhanced Protection}: Requires Water level 12. Your \tability{Spell Protection} ability activates when your current HP is 50\% of maximum, instead of 25\%. \\
\crystal{fire}{12pt} & %
\tspec{Desperate Blow}: Requires Fire level 12. You gain the Ranged Quick \tatk{physical} action \taction{Magic Ruin}. You may only use it if your current HP is 25\% of your max HP or less and if you have the \tstatus{Shell} status. To use it, you lose the \tstatus{Shell} status and launch a wave of energy. If you succeed in a weapon attack, the target loses MP equal to (your Max HP - your current HP), ignoring the target's ARM. Regardless of success, your Spell Protection will not activate during the rest of the combat. \\
\end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Dispel Magic}: Core Ability acquired at level 35. You gain the Slow (1) \tatk{magical} action \taction{Dispel Strike}. Perform a weapon attack. If successful, in addition to damage, you use your runes to absorb the target’s magic, ending all the target’s positive status effects. If he has \tstatus{Auto-status} or \tstatus{SOS-status}, these effects are suppressed until the end of the round. \pc

\begin{jobchoice}
\crystal{air}{12pt} & %
\tspec{Selective Dispel}: Requires Air level 16. Your \taction{Dispel Strike} ends all the target’s statuses, positive and negative, but you can choose which status effects you want to end, and which will continue. \\
\crystal{fire}{12pt} \crystal{water}{12pt} & %
\tspec{Anti-Magic Zone}: Requires Fire level 14 and Water level 12. When you use your \taction{Dispel Strike} action, you may target all other combatants, allies or enemies, but if you do, the action does not deal damage. \\
\end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
\noindent\tability{Return Magic}: Core Ability acquired at level 50. When you successfully use \taction{Runic} to block a Spell, you may discard an initiative die to cast the Spell you just blocked. You spend MP as usual, but you don’t need to have the Spell. \pc

\begin{jobchoice}
\crystal{water}{12pt} & %
\tspec{Triple Magic}: Requires Water level 18. You gain the reaction \taction{Triple Magic}. Use when suffering the effects of a Spell cast by an enemy. If, after suffering its effects, you may still cast Spells, spend MP equal to three times the Spell’s cost. If you do, you cast the Spell three times, each time against a random enemy target. Each target may be hit more than once. Even if the Spell originally targeted a group, when used with this reaction, it will affect a single target in each cast. \\
\crystal{earth}{12pt} & %
\tspec{Spell Ruin}: Requires Earth level 18. You gain the Quick \tatk{physical} action \taction{Spell Ruin}. Spend 10\% of your max MP and perform a weapon attack. If successful, deal 150\% weapon damage, and then the target loses a MP amount equal to the HP lost. \\
\end{jobchoice}
\end{ffminipage}
