\begin{multicols}{2}

\begin{ffcolpage}
    \begin{mobstats}[name=Guard Bot, level=5, type=construct, rank=common, earth=30,air=0,fire=15,water=15, hp=55, mp=10, arm=8, marm=0]
        \mobstatrow{ \tability{Ram}: Quick \tatk{physical} action, Earth vs Air, diff 40, 12 damage (\telem{Crush})  } 
        \mobstatrow{ \tability{Block}: Reaction, Earth vs Earth, diff 40, avoids a physical attack } 
        \mobstatrow{ \tstatus{Vulnerable: Lightning}} 
    \end{mobstats} 
    These small robots serve as sentries for various laboratories and industrial facilities. Their reinforced plates make them very strong against physical blows.
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Yellow Chocobo, level=6, type=beast, rank=common, earth=14,air=29,fire=20,water=18, hp=45, mp=21, arm=6, marm=4]
        \mobstatrow{ \tability{Beak}: Quick \tatk{physical} action, Air vs Air, diff 40, 6 damage (\telem{Puncture}) }
        \mobstatrow{ \tability{Dodge}: Reaction, Air vs Air, diff 70, avoids a \tatk{physical} attack}
        \mobstatrow{ \tspellblue{Choco Ball}: Blue Spell, 7 MP, Fire vs Water, diff 0, 10 damage (\telem{Crush})}
    \end{mobstats} 
    Bipedal ostrich-like birds, pony-sized, widely used as mounts. They are kind and friendly, but fierce when provoked.
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Imp, level=7, type=humanoid, rank=minion, earth=18,air=32,fire=12,water=22, hp=20, mp=15, arm=2, marm=5]
        \mobstatrow{ \tability{Short Sword}: Quick \tatk{physical} action, Air vs Earth, diff 40, 6 damage (\telem{Cut}) }
        \mobstatrow{ \tspellblue{Goblin Punch}: Blue Spell, 1 MP, Air vs Earth, diff 40, 6 damage (\telem{Cut}) or instead deals 24 damage (\telem{Cut}) against 7th level targets.}
    \end{mobstats} 
    Little green humanoids, usually malignant and territorial, who form tribes. They use improvised weapons and armor. They don't have great intelligence or physical strength but are very cunning.
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Venzuubius; Poison Demon, level=9, type=demon, rank=boss, earth=30,air=12,fire=40,water=19, hp=200, mp=150, arm=2, marm=2]
        \mobstatrow{ \tability{Mind Blast}: Quick \tatk{magical} action, Fire vs Water, diff 40, 12 damage (\telem{Crush}) }
        \mobstatrow{ \tability{Third Eye}: Reaction, Earth vs Earth, diff 40, blocks a melee attack }
        \mobstatrow{ \tspellblue{Flash}: Blue Spell, 14 MP, Fire vs Water, diff 0, 15 damage (\telem{Light}), if greater than dif 70, inflicts the \tstatus{Blind} status on the target until the end the round. }
        \mobstatrow{ \tspellblue{Poison Gas}: Blue Spell, 16 MP, Group, Fire vs Water, diff 70, inflicts the \tstatus{Poison} status on target until the end of next round. }
        \mobstatrow{ \tstatus{Vulnerable (Light)}, \tstatus{All Status Resist} }
    \end{mobstats} 
    One of the lesser Demon Lords, Venzuubius is arrogant and prideful. He acts with great overconfidence, treating his lesser brethren with disdain and his superiors with distrust. In battle, he tends to boast about his own abilities instead of quickly finishing his foes.
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Lesser Zombie, level=12, type=undead, rank=minion, earth=50,air=12,fire=35,water=31, hp=64, mp=40, arm=13, marm=11]
        \mobstatrow{ \tability{Slam}: Quick \tatk{physical} action, Earth vs Earth, diff 40, 20 damage (\telem{Crush}) }
        \mobstatrow{ \tspell{Poison}: Black Spell, 10 MP, Fire vs Water, diff 40, 15 damage (\telem{Bio}), inflicts the \tstatus{Poison} status on target until the end of the next round. }
        \mobstatrow{ \tstatus{Zombie}, \tstatus{Vulnerable (Fire)}, \tstatus{Vulnerable (Light)}, \tstatus{Ice Immune}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Reanimated carcasses of dead humanoids who blindly follow their dark masters. They are slow and devoid of free will.
\end{ffcolpage}

\begin{ffcolpage}
    \begin{mobstats}[name=Sahuagin Captain, level=15, type=aquatic, rank=elite, earth=42,air=45,fire=41,water=31, hp=270, mp=54, arm=5, marm=15]
        \mobstatrow{ \tability{Trident}: Quick \tatk{physical} action, Air vs Air, diff 40, 12 damage (\telem{Puncture}) }
        \mobstatrow{ \tability{Aqua Rage}: Quick Ranged \tatk{magical} action, Fire vs Water, diff 40, 24 damage (\taction{Water}) }
        \mobstatrow{ \tspell{Shell}: White Spell, 14 MP, Grants Shell until the end of next round. }
        \mobstatrow{ \tspell{Cure}: White Spell, 9 MP, Fire vs Water, diff 0, Heals 20 HP. }
        \mobstatrow{ \tstatus{Water Resist}, \tstatus{Lightning Weakness}, \tstatus{Weaken (Speed)}, \tstatus{Fatal Immune} }
    \end{mobstats} 
    Hybrids of men and fish, Sahuagins are led into battle by dangerous captains. They are slow on land, but powerful enemies.
\end{ffcolpage}

\end{multicols}