\section{Black Magic}\label{sec:magic-black}
\begin{multicols}{2}
    \subsection{Elemental Spells}\label{subsec:black-elemental}
    
    \textbf{Fire Group}: Elemental Spells whose main purpose is to deal Fire-elemental damage. There are four Fire spells:

	\textit{Fire}, acquired at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If you hit, deal 5 x Fire level \telem{Fire}-elemental magical damage to a target.
    
    \textit{Fira}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Fire}-elemental.
    
    \textit{Firaga}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Fire}-elemental.
    
    \textit{Meltdown}, acquired at level 55, costs 110 MP. Roll Fire vs Water, difficulty 0. If successful, deal 23 x Fire level \telem{Fire}-elemental magical damage level to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Meltdown} status on the target until the end of the round.
    
    \textbf{Ice Group}: Elemental Spells whose main purpose is to deal Ice-elemental damage. There are four Ice spells:
    
    \textit{Blizzard}, acquired at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Ice}-elemental magical damage to a target.
    
    \textit{Blizzara}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Ice}-elemental.
    
    \textit{Blizzaga}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Ice}-elemental.
    
    \textit{Freeze}, acquired at level 55, costs 110 MP. Roll Fire vs Water, difficulty 0. If successful, deal 23 x Fire level \telem{Ice}-elemental magical damage level to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Stop} status on the target until the end of the round.
    
    \textbf{Lightning Group}: Elemental Spells whose main purpose is to deal Lightning-elemental damage. There are four Lightning spells:
    
    \textit{Thunder}, gained at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Lightning}-elemental magical damage to a target.
    
    \textit{Thundara}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Lightning}-elemental.
    
    \textit{Thundaga}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Lightning}-elemental.
    
    \textit{Overcharge}, acquired at level 55, costs 110 MP. Roll Fire vs Water, difficulty 0. If successful, deal 23 x Fire level \telem{Lightning}-elemental magical damage level to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Berserk} status on the target until the end of the round.
    
    \subsection{Transmutation Spells}\label{subsec:black-transmutation}

    \textbf{Death Group}: Transmutation Spells whose primary purpose is to remove combat opponents as quickly as possible, or interfere with the target's ability to recover HP. There are four Death Spells:
    
    \textit{Sleep}, acquired at level 1, costs 7 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Sleep} status on the target until the end of the next round.
    
    \textit{Zombie}, acquired at level 19, costs 20 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Zombie} status on the target until the end of the next round.
    
    \textit{Condemn}, acquired at level 37, costs 60 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Condemn} status on the target until the end of the next round.
    
    \textit{Death}, acquired at level 55, costs 122 MP. Roll Fire vs Water, difficulty 70. If successful, the target is reduced to 0 HP. Treat this as a \tstatus{Fatal}–type status.
    
    \textbf{Transform Group}: Transmutation Spells whose primary purpose is to change the opponent’s form, to weaken it and reduce its combat power. There are four Transform Spells:
    
    \textit{Blind}, acquired at level 1, costs 6 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Blind} status on the target until the end of the next round.
    
    \textit{Petrify}, acquired at level 19, costs 23 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stone} status on the target at end of the next round.
    
    \textit{Toad}, acquired at level 37, costs 54 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Toad} status on the target until the end of the next round. This spell may also be used to remove the \tstatus{Toad} status from a target, instead.
    
    \textit{Stone}, acquired at level 55, costs 106 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stone} status on the target.
    
    \textbf{Poison Group}: Transmutation Spells whose primary purpose is to deal Bio damage. The more HP your enemy have, the more effective these Spells are. There are four Poison Spells:
    
    \textit{Poison}, acquired at level 1, costs 10 MP. Roll Fire vs Water, difficulty 40. If successful, deal 5 x Fire level \telem{Bio}-elemental magical damage to a target, and inflict the \tstatus{Poison} status on the target until the end of the next round.
    
    \textit{Bio}, acquired at level 19, costs 25 MP. Roll Fire vs Water, difficulty 40. If successful, deal 11 x Fire level \telem{Bio}-elemental magical damage to a target, and inflict the \tstatus{Poison} status on the target until the end of the next round.
    
    \textit{Venom}, acquired at level 37, costs 62 MP. Roll Fire vs Water, difficulty 40. If successful, deal 17 x Fire level \telem{Bio}-elemental magical damage to a target, and inflict the \tstatus{Poison} status on the target until the end of the next round.
    
    \textit{Virus}, acquired at level 55, costs 100 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Poison} and \tstatus{Virus} statuses on the target.
    
    \textbf{Water Group}: Worldly Spells whose main purpose is to deal Water-elemental damage. There are three Water spells:
    
    \textit{Water}, acquired at level 10, costs 15 MP. Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level \telem{Water}-elemental magical damage to a target.
    
    \textit{Waterga}, acquired at level 28, costs 40 MP. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level magical damage level to a target, or 8 x Fire level magical damage level to a group. This damage is \telem{Water}-elemental.
    
    \textit{Storm}, acquired at level 46, costs 80 MP. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level magical damage level to a target, or 12 x Fire level magical damage level to a group. This damage is \telem{Water}-elemental. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Sleep} status on the targets during this and the next two rounds.
    
    \subsection{Worldly Spells}\label{subsec:black-worldly}

    \textbf{Earth Group}: Worldly Spells whose main purpose is to deal Earth-elemental damage. There are three Earth spells:
    
    \textit{Magnitude}, acquired at level 10, costs 14 MP. Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level \telem{Earth}-elemental magical damage to all combatants who do not have the \tstatus{Float} or \tstatus{Flight} statuses. This Spell ignores \tstatus{Reflect}.
    
    \textit{Quake}, acquired at level 28, costs 43 MP. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Earth}-elemental magical damage to all combatants who do not have the \tstatus{Float} or \tstatus{Flight} statuses. This Spell ignores \tstatus{Reflect}.
    
    \textit{Break}, acquired at level 46, costs 84 MP. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{Earth}-elemental magical damage level to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Stone} status on the target until the end of the next round.
    
    \textbf{Shadow Group}: Worldly Spells whose main purpose is to deal Shadow-elemental damage. There are three Shadow spells:
    
    \textit{Dark}, acquired at level 10, costs 15 MP. Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level {Shadow}-elemental magical damage to a target.
    
    \textit{Scourge}, acquired at level 28, costs 39 MP. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level magical damage level to a target, or 8 x Fire level magical damage level to a group. This damage is {Shadow}-elemental.
    
    \textit{Scathe}, acquired at level 46, costs 85 MP. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level magical damage level to a target, or 12 x Fire level magical damage level to a group. This damage is \telem{Shadow}-elemental. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Blind} status on the targets during this and the next two rounds.
    
    \subsection{Expert Spells}\label{subsec:black-expert}

    \textbf{Mage Bane Group}: Expert Spells whose main purpose is to manipulate MP, weakening enemy magicians, and to restore the user's MP. There are two Mage Bane Spells:
    
    \textit{Rasp}, acquired at level 30, costs 42 MP. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{non}-elemental magical damage to a target. This Spell damages MP instead of HP.
    
    \textit{Osmosis}, acquired at level 50, costs 45 MP. Roll Fire vs Water, difficulty 50. If successful, deal 16 x Fire level \telem{non}-elemental magical damage to a target. This Spell damages MP instead of HP. The caster recovers MP equal to the damage dealt.
    
    \textbf{Drain Group}: Expert Spells whose main purpose is to recover the user's HP, through the ability to steal the target’s life. There are two Drain Spells:
    
    \textit{Drain}, acquired at level 30, costs 42 MP. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Puncture}-elemental magical damage to a target. 50\% of damage dealt is recovered in HP by the user.
    
    \textit{Syphon}, acquired at level 50, costs 90 MP. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{Puncture}-elemental magical damage to a target. 50\% of damage dealt is recovered in HP by the user.
    
    \textbf{Hex Group}: Expert Spells whose main purpose is to weaken the target, causing several negative statuses at the same time. There are two Hex Spells:
    
    \textit{Pain}, acquired at level 30, costs 40 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Blind}, \tstatus{Poison} and \tstatus{Slow} statuses on the target until the end of next round.
    
    \textit{Curse}, acquired at level 50, costs 96 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Mute}, \tstatus{Immobilize} and \tstatus{Disable} statuses on the target until the end of next round.
    
    \subsection{Black Mysteries}\label{subsec:black-mysteries}

    \textbf{Black Mysteries}: Black magic arcane mysteries are the most destructive. All of them deal damage, being the most damaging spells available to any mage. Mysteries are not a Spell group and cannot be chosen as such.
    
    \textit{Doomsday}, acquired at level 64, cost 160 MP. Roll Fire vs Water, difficulty 0. If successful, deal 28 x Fire level \telem{Shadow}-elemental magical damage to a group. Also, if your roll overcomes difficulty 70, the targets are reduced to 0 HP. Treat this as a \tstatus{Fatal}-type status.  This spell ignores \tstatus{Reflect}.
    
    \textit{Flare}, acquired at level 64, costs 150 MP. Roll Fire vs Water, difficulty 0. If successful, deal 35 x Fire level \telem{non}-elemental magical damage to a target. This spell ignores \tstatus{Reflect}, \tstatus{Shell} and the target’s Magic Armor.  
    
    \textit{Ultima}, acquired the 64 level, cost 170 MP. Roll Fire vs Water, difficulty 0. If successful, deal 30 x Fire level \telem{non}-elemental magical damage to a group. This spell ignores \tstatus{Reflect} and \tstatus{Shell}. 

\end{multicols}

\section{White Magic}\label{sec:magic-white}

\begin{multicols}{2}
	
    \textbf{Healing Group}: These spells restore lost HP. They are the hallmark of White Mages. These Spells have no effect on targets with exactly zero HP. There are four Healing Spells:

    \textit{Cure}, acquired at level 1, costs 9 MP. Roll Fire vs Water, difficulty 0. On success, restore 5 x Fire level HP on a target.

    \textit{Cura}, acquired at level 19, costs 28 MP. Roll Fire vs Water, difficulty 0. On success, restore 11 x Fire level HP on a target or 7x Fire level HP on a group.

    \textit{Curaga}, acquired at level 37, costs 65 MP. Roll Fire vs Water, difficulty 0. On success, restore 17 x Fire level HP on a target or 10x Fire level HP on a group.

    \textit{Renew}, acquired at level 55, costs 115 MP. Roll Fire vs Water, difficulty 0. If successful, the target is healed an amount of HP equal to its maximum HP. If the target is under the \tstatus{Zombie} status effect, the difficulty is increased to 50 and this spell reduce the target’s current HP to 1.

    \subsection{Heavenly Spells}\label{subsec:white-heavenly}

    \textbf{Purify Group}: Heavenly Spells that remove negative statuses. They are an important aid to keep the group’s fighting condition. There are four Purify Spells:

    \textit{Poisona}, acquired at level 1, costs 6 MP. Roll Fire vs Water, difficulty 0. If successful, the target loses the \tstatus{Poison} and \tstatus{Virus} statuses.

    \textit{Basuna}, acquired at level 19, costs 20 MP. Roll Fire vs Water, difficulty 0. If successful, the target loses the \tstatus{Stone}, \tstatus{Blind}, \tstatus{Mute}, \tstatus{Disable} and \tstatus{Immobilize} statuses.

    \textit{Esuna}, acquired at level 37, costs 65 MP. Roll Fire vs Water, difficulty 0. If successful, the target loses all negative statuses.

    \textit{Vaccine}, acquired at level 55, costs 130 MP. Roll Fire vs Water, difficulty 0. If successful, the group loses all negative statuses.

    \textbf{Air Group}: Heavenly Spells whose main purpose is to deal Air-elemental damage. There are four Air spells:

    \textit{Aero}, acquired at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Air}-elemental magical damage to a target.

    \textit{Aera}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Air}-elemental.

    \textit{Aeraga}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Air}-elemental.

    \textit{Whirlwind}, acquired at level 55, costs 120 MP. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{Air}-elemental magical damage to a group.

    \textbf{Light Group}: Heavenly Spells whose main purpose is to deal Light-elemental damage. There are four Light spells:

    \textit{Banish}, acquired at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Light}-elemental magical damage to a target.

    \textit{Banishra}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Light}-elemental.

    \textit{Banishga}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Light}-elemental.

    \textit{Fade}, acquired at level 55, costs 110 MP. If successful, deal 23 x Fire level \telem{Light}-elemental magical damage level to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Mute} status on the target until the end of the next round.

    \subsection{Protective Spells}\label{subsec:white-protective}

    \textbf{Elemental Group}: Protective Spells whose main purpose is to protect the mage and his allies from elemental damage. Whenever you cast these Spells, choose an element: \telem{Fire}, \telem{Ice}, \telem{Lightning}, \telem{Water}, \telem{Earth}, \telem{Shadow}, \telem{Bio}, \telem{Air} or \telem{Light}. There are four Elemental spells:

    \textit{Resist}, acquired at level 10, costs 14 MP. Roll Fire vs Water, difficulty 0. On success, grant the \tstatus{Resist} (chosen element) status to a target until the end of the next round.

    \textit{Immune}, acquired at level 28, costs 35 MP. Roll Fire vs Water, difficulty 0. On success, grant the \tstatus{Immune} (chosen element) status to a target until the end of the next round.

    \textit{Absorb}, acquired at level 46, costs 75 MP. Roll Fire vs Water, difficulty 0. On success, grant the \tstatus{Absorb} (chosen element) status to a target until the end of the next round.

    \textbf{Life Group}: Protective Spells whose main purpose is to keep the mage and his allies alive, rendering them able to fight after falling to 0 HP. There are three Life Spells:

    \textit{Raise}, acquired at level 10, costs 19 MP. Roll Fire vs Water, difficulty 0. If successful, the zero HP target is healed to 10\% of its maximum HP. If used on a target with the \tstatus{Zombie} status, the difficulty is 90 instead of 0, and, if successful, the target is reduced to zero HP instead of healed.

    \textit{Reraise}, acquired at level 28, costs 50 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Reraise} status to target during this and the next two rounds.

    \textit{Arise}, acquired at level 46, costs 100 MP. Roll Fire vs Water, difficulty 0. If successful, the zero HP target is healed to 100\% of its maximum HP. If used on a target with the \tstatus{Zombie} status, the difficulty is 60 instead of 0, and, if successful, the target is reduced to zero HP instead of healed.

    \textbf{Armor Group}: Protective Spells whose main purpose is to defend the mage and his allies from physical damage. There are three Armor Spells:

    \textit{Protect}, acquired at level 10, costs 14 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Protect} status to a target until the end of next round.

    \textit{Protectga}, acquired at level 28, costs 40 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Protect} status to a group until the end of next round.

    \textit{Wall}, acquired at level 46, costs 92 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Wall} status to a target until the end of next round.

    \textbf{Shield Group}: Protective Spells whose main purpose is to defend the mage and his allies from magical damage. There are three Shield Spells:

    \textit{Shell}, acquired at level 10, costs 14 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Shell} status to a target until the end of next round.

    \textit{Shellga}, acquired at level 28, costs 40 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Shell} status to a group until the end of next round.

    \textit{Reflect}, acquired at level 46, costs 92 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Reflect} status on a target until the end of next round.

    \textbf{Images Group}: Protective Spells whose main purpose is to defend the mage and his allies, making them harder to hit. It is more effective in stopping high difficulty attacks. There are three Images Spells:

    \textit{Blink}, acquired at level 10, costs 14 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Blink} status to a target until the end of next round.

    \textit{Ruse}, acquired at level 28, costs 40 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Blink} status to a group until the end of next round.

    \textit{Vanish}, acquired at level 46, costs 82 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Vanish} status to a target until the end of next round.

    \subsection{Psychic Spells}\label{subsec:white-psychic}

    \textbf{Enchantment Group}: Psychic Spells whose main purpose is to prevent your opponents from using spells or special actions. It is an effective tool to facilitate the fighting by removing enemies’ options. There are two Enchantment Spells:

    \textit{Silence}, acquired at level 30, costs 30 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Mute} status on the target until the end of the next round.

    \textit{Berserk}, acquired at level 50, costs 84 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Berserk} status on the target until the end of the next round.

    \textbf{Madness Group}: Psychic Spells whose main purpose is to confuse opponents, causing them to fight in favor of the caster. Although powerful, they are easily undone. There are two Madness Spells:

    \textit{Confuse}, acquired at level 30, costs 38 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Confuse} status on the target until the end of the next round.

    \textit{Charm}, acquired at level 50, costs 89 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Charm} status on the target until the end of the next round.

    \textbf{Vulnerability Group}: Psychic Spells whose main purpose is to find or create elemental weaknesses. They aren’t powerful offensive Spells by themselves but can greatly increase the damage of other attacks. There are two Vulnerability Spells:

    \textit{Scan}, acquired at level 30, costs 30 MP. Roll Fire vs Water, difficulty 40. If successful, you discover the maximum and current HP and MP of the target as well as their Stat levels, their status effects Vulnerabilities, Resistances and Immunities and their elemental Vulnerabilities, Resistances and Immunities and Absorptions.

    \textit{Weaken}, acquired at level 50, costs 82 MP. Roll Fire vs Water, difficulty 70. If successful, choose an element: \telem{Fire}, \telem{Ice}, \telem{Lightning}, \telem{Water}, \telem{Earth}, \telem{Shadow}, \telem{Bio}, \telem{Air} or \telem{Light}. The target receives the status \tstatus{Vulnerability} to the chosen element to the end of the next round. 

    \subsection{White Mysteries}\label{subsec:white-mysteries}

    \textbf{White Mysteries}: White magic arcane mysteries protect and attack, and can complete the White Mage's arsenal, either going specialist or generalist. Mysteries are not a Spell group and cannot be chosen as such.

    \textit{Holy}, acquired at level 64, cost 155 MP. Roll Fire vs Water, difficulty 0. If successful, deal 30 x Fire level \telem{Light}-elemental magical damage to a target.  

    \textit{Rebirth}, acquired at level 64, cost 160 MP. Choose a group. Roll Fire vs Water, difficulty 0. All characters hit in that group who have zero HP are healed to 100\% of their maximum HP. For each character in that group with the \tstatus{Zombie} status, the difficulty is 60 instead of 0, and, if successful, the target is reduced to zero HP instead of healed.

    \textit{Shield}, acquired at level 64, cost 150 MP. Roll Fire vs Water, difficulty 0. If successful, the target becomes immune to all damage until the end of next round.


\end{multicols}

\section{Time Magic}\label{sec:magic-time}

\begin{multicols}{2}
    
    \subsection{Astral Spells}\label{subsec:time-astral}

    \textbf{Cosmic Group}: Astral Spells whose main purpose is to deal Cut-elemental damage. It is the only reliable Spell a Time Mage may use to deal group-target damage. There are four Astral spells:
    
    \textit{Burn Ray}, acquired at level 1, costs 8 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Cut}-elemental magical damage to a target.
    
    \textit{Ray Bomb}, acquired at level 19, costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level magical damage level to a target, or 7 x Fire level magical damage level to a group. This damage is \telem{Cut}-elemental.
    
    \textit{Quasar}, acquired at level 37, costs 58 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level magical damage level to a target, or 10 x Fire level magical damage level to a group. This damage is \telem{Cut}-elemental.
    
    \textit{Shockwave Pulsar}, acquired at level 55, costs 112 MP. Roll Fire vs Water, difficulty 0. If successful, deal 23 x Fire level magical damage level to a target, or 17 x Fire level magical damage level to a group. This damage is \telem{Cut}-elemental.
    
    \textbf{Teleport Group}: Astral Spells whose main purpose is to avoid combat. It may be used either to escape fights or to teleport away the opponents. There are four Teleport Spells:
	
    \textit{Escape}, acquired at level 1, costs 7 MP. Teleports you to a location that can see at a maximum distance of 2 x Fire level meters. If used in combat, you can flee if succeed in a Fire vs Air roll, difficulty 0. Treat this as using the \taction{Flee} action.
    
    \textit{Teleport}, acquired at level 19, costs 21 MP. Your group teleports to a location that you can see at a maximum distance of 5 x Fire level meters. If used in combat, your group can flee if you succeed in a Fire vs Air roll, difficulty 0. Treat this as using the \taction{Flee} action.
    
    \textit{Remove}, acquired at level 37, costs 50 MP. Roll Fire vs Water, difficulty 70. If successful, the target is teleported to an unknown location away from the combat. This counts as if it had fled the battle. Treat this effect a \tstatus{Time}-type negative status effect.
    
    \textit{X-Zone}, acquired at level 55, costs 103 MP. Roll Fire vs Water, difficulty 70. If successful, the enemy group is teleported to an unknown location away from the combat. This counts as if they had fled the battle. Treat this effect a \tstatus{Time}-type negative status effect.
    
    \textbf{Gravity Group}: Astral Spells whose main purpose is to deal damage. Damage is based on the target’s current HP, being more efficient the less damage the target has suffered. As it counts as status effects rather than as damage, it can be easily canceled by immunities or resistances. There are four Gravity Spells:
    
    \textit{Gravity}, acquired at level 1, costs 9 MP. Roll Fire vs Water, difficulty 25. If successful, the target loses 25\% of its current HP. This is a \tstatus{Gravity} status effect.
    
    \textit{Demi}, acquired at level 19, costs 27 MP. Roll Fire vs Water, difficulty 50. If successful, the target loses 50\% of its current HP. This is a \tstatus{Gravity} status effect.
    
    \textit{Quarter}, acquired at level 37, costs 63 MP. Roll Fire vs Water, difficulty 75. If successful, the target loses 75\% of its current HP. This is a \tstatus{Gravity} status effect.
    
    \textit{Black Hole}, acquired at level 55, costs 123 MP. Roll Fire vs Water, difficulty 99. If successful, the target is reduced to exactly 1 HP. This is a \tstatus{Gravity} status effect.
    
    \subsection{Subtle Spells}\label{subsec:time-subtle}

    \textbf{Slow Group}: Subtle Spells whose main purpose is to prevent the target’ actions. Unable to act, the target becomes easy prey. There are four Slow Spells:
    
    \textit{Yawn}, acquired at level 1, costs 6 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Speed)} status on the target over the next two rounds. When casting, you may reduce the spell's duration by 1 round to increase all target's current initiative dice's values by 1, to a maximum of 10.
    
    \textit{Slow}, acquired at level 19, costs 22 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Slow} status on the target over the next two rounds.
    
    \textit{Slowga}, acquired at level 37, costs 54 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Slow} status on the group over the next two rounds.
    
    \textit{Stop}, acquired at level 55, costs 101 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stop} status on the target until the end of next round.
    
    \textbf{Weaken Group}: Subtle Spells whose main purpose is to decrease the damage dealt or endured by the target. Thus, it is a versatile group, possessing a blend of offensive and defensive spells. There are four Weaken Spells:
    
    \textit{Mental Down}, acquired at level 1, costs 20 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Mental)} status on the target until the end of next round.
    
    \textit{Armor Down}, acquired at level 19, costs 20 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Armor)} status on the target until the end of next round.
    
    \textit{Power Down}, acquired at level 37, costs 50 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Physical)} status on the target until the end of next round.
    
    \textit{Magic Down}, acquired at level 55, costs 50 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Magic)} status on the target until the end of next round.
    
    \textbf{Strengthen Group}: Subtle Spells whose main purpose is to increase the damage dealt or endured by the target. Thus, it is a versatile group, possessing a blend of offensive and defensive spells. There are four Strengthen Spells:
    
    \textit{Mental Up}, acquired at level 1, costs 20 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Strengthen (Mental)} status to the target until the end of next round.

    \textit{Armor Up}, acquired at level 19, costs 20 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Strengthen (Armor)} status to the target until the end of next round.
    
    \textit{Power Up}, acquired at level 37, costs 50 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Strengthen (Physical)} status to the target until the end of next round.
    
    \textit{Magic Up}, acquired at level 55, costs 50 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Strengthen (Magic)} status to the target until the end of next round.
    
    \textbf{Flight Group}: Subtle Spells whose main purpose is to deal with winged opponents. With these spells, you can stick a flying opponent to the ground or have an ally fly out of reach of its opponents. There are four Flight Spells:
    
    \textit{Speed Up}, acquired at level 1, costs 6 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Strengthen (Speed)} status to the target until the end of next round. When casting, you may reduce the spell's duration by 1 round to reduce all target's current initiative dice's values by 1, to a minimum of the current phase.
    
    \textit{Float}, acquired at level 19, costs 23 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Float} status to the group until the end of next round.
    
    \textit{Tractor}, acquired at level 37, costs 50 MP. Roll Fire vs Water, difficulty 40. If successful, the target loses the \tstatus{Float} and \tstatus{Flight} statuses and may not gain them until the end of the next round.
    
    \textit{Flight}, acquired at level 55, costs 95 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Flight} status to the target until the end of next round.
    
    \subsection{Void Spells}\label{subsec:time-void}

    \textbf{Meteor Group}: Void Spells whose main purpose is to deal Crush-elemental damage. It is especially powerful against enemies with high magical defense, as they ignore the target’s Magic Armor. There are three Meteor Spells:
    
    \textit{Meteorite}, acquired at level 10, costs 15 MP. Roll Fire vs Water two times, difficulty 0. For each success, deal 4 x Fire level \telem{Crush}-elemental magical damage to a random enemy. This spell ignores \tstatus{Reflect} and the target’s Magic Armor.
    
    \textit{Comet}, acquired at level 28, costs 41 MP. Roll Fire vs Water three times, difficulty 0. For each success, deal 4 x Fire level \telem{Crush}-elemental magical damage to a random enemy. This spell ignores \tstatus{Reflect} and the target’s Magic Armor.
    
    \textit{Meteo}, acquired at level 46, costs 79 MP. Roll Fire vs Water five times, difficulty 0. For each success, deal 4 x Fire level \telem{Crush}-elemental magical damage to a random enemy. This spell ignores \tstatus{Reflect} and the target’s Magic Armor.
    
    \textbf{Speed Group}: Void Spells whose main purpose is to allow more actions to your allies. Increasing the amount of target’s initiative dice, you can multiply your effectiveness in combat. There are three Speed Spells:
    
    \textit{Haste}, acquired at level 10, costs 17 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Haste} status to the target over the next two rounds.
    
    \textit{Hastega}, acquired at level 28, costs 42 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Haste} status to the group over the next two rounds.
    
    \textit{Quicken}, acquired at level 46, costs 91 MP. You gain two extra initiative dice, with value equal to the current phase.
    
    \subsection{Inspiration Spells}\label{subsec:time-inspiration}

    \textbf{Regeneration Group}: Inspiration Spells whose main purpose is to heal and protect. It is a balanced group who may be used both offensively and defensively. There are two Regeneration Spells:
    
    \textit{Regen}, acquired at level 30, costs 30 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Regen} status to the target on this and the next two rounds.
    
    \textit{Temporal Shift}, acquired at level 50, costs 80 MP. Roll Fire vs Water, difficulty 0. On success, all combatants, enemies and allies, lose their \tstatus{Time}-type status effects, whether positive or negative.
    
    \textbf{Paralysis Group}: Inspiration Spells whose main purpose is to prevent the opponent to attack or react. It is a highly defensive group, reducing the target’s ability to fight. There are two Paralysis spells:
    
    \textit{Immobilize}, acquired at level 30, costs 33 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Immobilize} status on the target until the end of next round.
    
    \textit{Disable}, acquired at level 50, costs 76 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Disable} status on the target until the end of next round.
    
    \textbf{Divination Group}: Inspiration Spells whose main purpose is to increase the success of the target’s actions. It is a primarily offensive group, lessening the failure chance of your allies’ actions. There are two Divination Spells:
    
    \textit{Reset}, acquired at level 30, costs 31 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Premonition} status to the target until the end of next round.
    
    \textit{Return}, acquired at level 50, costs 75 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Premonition} status to the group until the end of next round.
    
    \subsection{Time Mysteries}\label{subsec:time-mysteries}

    \textbf{Time Mysteries}: Time magic arcane mysteries are mostly offensive, although only one of them deal damage. The Time Wizard should choose the mystery that better complements its function to support his teammates, which varies depending on the group’s composition and personality. Mysteries are not a Spell group of and may not be chosen as such.
    
    \textit{Meteor}, acquired the 64 level, cost 155 MP. Roll Fire vs Water eight times, difficulty 0. For each success, deal 4 x Fire level \telem{Crush}-elemental magical damage to a random enemy. This spell ignores \tstatus{Reflect} and the target’s Magic Armor.
    
    \textit{Old}, acquired the 64 level, cost 150 MP. Roll Fire vs Water, difficulty 70. If successful, the target takes the statuses \tstatus{Weaken (Speed)}, \tstatus{Weaken (Armor)}, \tstatus{Weaken (Mental)}, \tstatus{Weaken (Magic)} and \tstatus{Weaken (Physical)} during this and the next two rounds.
    
    \textit{Time Stop}, acquired the 64 level, cost 160 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stop} status on the group until the end of next round.

\end{multicols}

\section{Blue Magic}\label{sec:magic-blue}
\begin{multicols}{2}

Blue Magic is classified in four main types, from the weakest to the strongest: Initiate, Acolyte, Master and Ancient. Unlike other Spells, they do not have minimum levels and may be cast as soon as the character learn the Spell, provided they have the required Core Ability. They also may not be cast by \textit{Arcane Focus, Spell Weave} or \textit{Critical Spell}.
 
\subsection{Initiate Spells}\label{subsec:blue-initiate}
	When creating a Druid character that casts Blue Magic, your starting spells must come from this category. They are appropriate for 1st to 15th levels.

    \textit{Choco Ball} costs 7 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Crush}-elemental magical damage to a target.

    \textit{Death Force} costs 12 MP. Roll Fire vs Water, difficulty 0. If successful, the target becomes resistant to all \tstatus{Fatal}-type status effects until the end of next round.

	\textit{Flash} costs 14 MP. Roll Fire vs Water, difficulty 0. If successful, deal 5 x Fire level \telem{Light}-elemental magical damage to a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Blind} status on the target until the end the round.
	
    \textit{Goblin Punch} costs 1 MP. Perform a weapon attack, difficulty 50. If successful, deal weapon damage to a target. If you have the same character level as the target, deal extra damage equal to three times weapon damage. This Spell does physical damage, can’t hit targets under the \tstatus{Flight} status unless you have it and ignores the \tstatus{Reflect} status.

    \textit{Hastebreak} costs 8 MP. Roll Fire vs Water, difficulty 40. If the target has the \tstatus{Strengthen (Speed)} status, it loses it and receives the \tstatus{Weaken (Speed)} status over the next two rounds. If the target has the \tstatus{Haste} status, he loses it and receives the \tstatus{Slow} status over the next two rounds. This spell has no effect on targets that doesn’t have the two above mentioned status effects.
    
    \textit{Nightsong} costs 20 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Sleep} status on a group until the end of the next round.
    
    \textit{Poison Gas} costs 16 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Poison} status on a group until the end of the next round.
    
    \textit{Red Feast} costs 10 MP. Make a weapon attack, difficulty 0. If successful, deal 5x Fire level \telem{Puncture}-elemental damage. You recover HP equal to half damage dealt, before accounting enemy Armor. This Spell can’t hit targets under the \tstatus{Flight} status unless you have it and ignores the \tstatus{Reflect} status.
    
    \textit{Self-Destruct} costs 1 MP. Roll Fire vs Water, difficulty 0. If successful, deal \telem{non}-elemental magic damage equal to your current HP to the target. After using this Spell, you lose the \tstatus{Reraise} status and are reduced to 0 HP. No immunities can prevent you from being reduced to 0 HP in this way. Do not add the singles digit to the damage dealt.

    \textit{Transfusion} costs 1 MP. Roll Fire vs Water, difficulty 0. If successful, restore a HP amount equal to your current HP to the target. After using this Spell, you lose the \tstatus{Reraise} status and are reduced to 0 HP. No immunities can prevent you from being reduced to 0 HP in this way. Do not add the singles digit to the HP healed.
    
\subsection{Acolyte Spells}\label{subsec:blue-acolyte}

These more powerful spells begin to reveal the true power of Blue Mage. They are appropriate for 16th to 30th levels.

    \textit{1000 Needles} costs 35 MP. Roll Fire vs Water, difficulty 0. If successful, the target suffers 100 damage. This Spell ignores the target’s magic armor, \tstatus{Shell} and \tstatus{Reflect}.

    \textit{Acid} costs 63 MP. Roll Fire vs Water, difficulty 0. If successful, deal 18 x Fire level \telem{Bio}-elemental magical damage on a target. Also, if your roll overcomes difficulty 70, inflict the \tstatus{Weaken (Mental)} and \tstatus{Weaken (Armor)} on the target until the end of the next round.
    
    \textit{Degenerator} costs 32 MP. Roll Fire vs Water, difficulty 70. If successful, until the end of the next round, every time the target performs a physical attack it loses HP equal to 10\% of his current HP and each time the target performs a magical attack or Spell it loses MP equal to 10\% of his current MP. Ignore armor, magic armor and any of the target’s status when it suffers this damage. This counts as a \tstatus{Toxic}-type status.
    
    \textit{Dragon Force} costs 45 MP. Roll Fire vs Water, difficulty 0. If successful, grant the \tstatus{Resist} (Fire, Ice and Lightning) status to a group until the end of next round.
    
    \textit{Flame Thrower} costs 24 MP. Roll Fire vs Water, difficulty 0. If successful, deal 12 x Fire level \telem{Fire}-elemental damage to a target.
    
	\textit{Force Field} costs 35 MP. Roll Fire vs Water, difficulty 0, against a group. Roll 1d10: 1: \telem{Fire}; 2: \telem{Ice}; 3: \telem{Lightning}; 4: \telem{Earth}; 5: \telem{Air}; 6: \telem{Water}; 7: \telem{Bio}; 8: \telem{Light}; 9: \telem{Shadow}; 0: None. Grant the (Element) \tstatus{Immune} status for each character hit based on the d10 roll, until the end of the next round.
    
    \textit{Magic Hammer} costs 30 MP. Roll Fire vs Water, difficulty 50. If successful, deal \telem{non}-elemental magical damage to the target equal to half of its current MP. The target loses MP instead of HP when suffering this Spell. This spell ignores the target’s Magic Armor.
    
    \textit{Matra Magic} cost 55 MP. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level damage to a target, or 10x Fire level damage to a group. This Spell does \telem{Fire}-elemental magical damage.

    \textit{Seed Cannon} costs 22 MP. Roll Fire vs Water, difficulty 0. If successful, deal 11 x Fire level damage to a target, or 7x Fire level damage to a group. This Spell does \telem{Puncture}-elemental physical damage and ignores the \tstatus{Reflect} status.
    
    \textit{Stare} costs 60 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Confuse} status to a group until the end of the next round.
    
\subsection{Master Spells}\label{subsec:blue-master}

	At this level there are some of the most powerful Blue Magic Spells, showcasing all the power of nature. They are appropriate to 31st to 50th levels.

    \textit{Aqua Rake} costs 85 MP. Roll Fire vs Water, difficulty 0. If successful, deal 13 x Fire level \telem{Water}-elemental magical damage level to a group. This Spell ignores the \tstatus{Reflect} status.

    \textit{Death Claw} costs 110 MP. Roll Fire vs Water, difficulty 80. If successful, the target's HP is reduced to the d100’s singles digit, considering 0 as 10. Treat this as a \tstatus{Gravity} status effect.
    
    \textit{Earth Shake} costs 67 MP. Roll Fire vs Water, difficulty 0. Roll Fire vs Water, difficulty 0. If successful, deal 13 x Fire level \telem{Earth}-elemental magical damage level to a group. This Spell ignores the \tstatus{Reflect} status and automatically fails against targets under the \tstatus{Float} or \tstatus{Flight} status effects.
    
    \textit{Electrocute} costs 85 MP. Roll Fire vs Water, difficulty 0. If successful, deal 13 x Fire level \telem{Lightning}-elemental magical damage level to a group. This Spell ignores the \tstatus{Reflect} status.
    
    \textit{Frog Song} costs 100 MP. Roll Fire vs Water, difficulty 70, twice, against a group. Heal from or inflict the \tstatus{Toad} status until the end of the next round on each target hit by the first roll. Inflict the \tstatus{Sleep} status until the end of the next round on each target hit by the second roll.
    
    \textit{Level 3 Confuse} costs 65 MP. Roll Fire vs Water, difficulty 30. Inflict the \tstatus{Confuse} status until the end of the next round on all enemies hit whose level is a multiple of three. This Spell ignores the \tstatus{Reflect} status.
    
    \textit{Rippler} costs 74 MP. Roll Fire vs Water, difficulty 40. If successful, you and the target exchange any status effects, keeping their respective durations. For example, a \tstatus{Blind} Druid use this spell on a \tstatus{Haste} and \tstatus{Immobilize} target becomes \tstatus{Haste} and \tstatus{Immobilize}, while the target becomes \tstatus{Blind}. This spell does not affect status effects that are caused by permanent effects, such as equipment with Auto-Status or SoS-Status or permanent Abilities.
    
    \textit{Roulette} costs 70 MP. Pick a random combatant (ally, enemy or the caster). Roll Fire vs Water, difficulty 40. If successful, it is reduced to 0 HP. Treat this as a \tstatus{Fatal}-type status. This Spell ignores the \tstatus{Reflect} status.
    
	\textit{Wall Change} costs 72 MP. Roll Fire vs Water, difficulty 70. If successful, grant the target the (Element) \tstatus{Resist} to all elements, except one random element. To find the random element, roll 1d10: 1: \telem{Fire}; 2: \telem{Ice}; 3: \telem{Lightning}; 4: \telem{Earth}; 5: \telem{Air}; 6: \telem{Water}; 7: \telem{Bio}; 8: \telem{Light}; 9: \telem{Shadow}; 0: \telem{Cut}, \telem{Crush} and \telem{Puncture}. He also receives the (Element) \tstatus{Vulnerable} to all elements it does not have resistance, immunity or absorption. The element to which the target is vulnerable randomly changes every five phases. This effect lasts this and the next two rounds.
    
    \textit{White Wind} costs 99 MP. Roll Fire vs Water, difficulty 0. On success, all allies recover a HP amount equal to your current HP. You do not recover HP with this Spell.

\subsection{Ancient Spells}\label{subsec:blue-ancient}

	These spells are usually found only at very high levels, representing the maximum power of Blue Magic. They are appropriate from 51st level onward.
    
    \textit{Bad Breath} costs 130 MP. Roll Fire vs Water, difficulty 70 against the enemy group. For each enemy hit, roll 1d10. Inflict all status listed below to each enemy until the end of next round according to its d10 roll.

1-2: \tstatus{Immobilize}, \tstatus{Mute}, \tstatus{Poison}, \tstatus{Meltdown}.

3-4: \tstatus{Blind}, \tstatus{Disable}, \tstatus{Poison}, \tstatus{Slow}.

5-6: \tstatus{Confuse}, \tstatus{Slow}, \tstatus{Virus}, \tstatus{Toad}.

7-8: \tstatus{Confuse}, \tstatus{Condemn}, \tstatus{Slow}, \tstatus{Poison}.

9-0: \tstatus{Berserk}, \tstatus{Blind}, \tstatus{Poison}, \tstatus{Zombie}.

    \textit{Grand Train} costs 160 MP. Roll Fire vs Water, difficulty 0. If successful, deal 30 x Fire level \telem{non}-elemental magical damage to a group. This Spell ignores the \tstatus{Reflect} status.
    
    \textit{Level 2 Old} cost 155 MP. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Weaken (Armor)}, \tstatus{Weaken (Mental)}, \tstatus{Weaken (Magic)} and \tstatus{Weaken (Physical)} status effects on all even level enemies until the end of the next round. This Spell ignores the \tstatus{Reflect} status.
    
    \textit{Level 4 Flare} costs 145 MP. Roll Fire vs Water, difficulty 0. If successful, deal 33 x Fire level \telem{non}-elemental magical damage to all enemies whose level is a multiple of four. This Spell ignores the \tstatus{Shell} and \tstatus{Reflect} status effects.
    
    \textit{Level 5 Death} costs 130 MP. Roll Fire vs Water, difficulty 30. All enemies hit whose level is a multiple of five are reduced to 0 HP. Treat this as a \tstatus{Fatal}-type status. This Spell ignores the \tstatus{Reflect} status.
    
    \textit{Magic Breath} costs 120 MP. Roll Fire vs Water, difficulty 0, three times, against a group. Deal 8 x Fire level \telem{Fire}-elemental magical damage on each target hit by the first roll. Deal 8 x Fire level \telem{Ice}-elemental magical damage on each target hit by the second roll. Deal 8 x Fire level \telem{Lightning}-elemental magical damage on each target hit by the third roll. This Spell ignores the target’s Magic Armor.
    
    \textit{Mighty Guard} costs 140 MP. You and all your allies gain the \tstatus{Haste}, \tstatus{Protect}, and \tstatus{Shell} status effects during this and the next two rounds.
    
    \textit{Shadow Flare} costs 161 MP. Roll Fire vs Water, difficulty 0. If successful, deal 33 x Fire level \telem{Shadow}-elemental magical damage to a target.
    
    \textit{Stone Breath} costs 115 MP. Roll Fire vs Water, difficulty 70, against a group. Inflict the \tstatus{Stone} status until the end of the next round on each target hit.
    
	\textit{Supernova} costs 175 MP. Roll Fire vs Water, difficulty 0. If successful, deal 8 x character level \telem{non}-elemental magical damage to a group. This Spell ignores the \tstatus{Reflect} status.

\end{multicols}
\section{Other Spells}\label{sec:magic-other}
\begin{multicols}{2}

    These spells give some specific Secondary Jobs some capabilities that complement their skills. The Berserker learn one of these Spells at advanced level, and the Defender may eventually learn one, two or even three of these Spells. These Spells are not a Spell group of and may not be chosen as such.
    
    \textit{Astra}, acquired at level 30, costs 35 MP. Roll Fire vs Water, difficulty 0. If successful, the target becomes immune to all negative status effects until the end of the round.
    
    \textit{Dispel}, acquired at level 40, costs 60 MP. Roll Fire vs Water, difficulty 40. If successful, the target loses all the positive status effects. If he has Auto-Status or SOS-Status, these effects are disabled until the end of the round. This spell ignores \tstatus{Reflect}.
    
    \textit{Astraga}, acquired at level 50, costs 85 MP. Roll Fire vs Water, difficulty 0. If successful, the group becomes immune to all negative status effects until the end of the round.
    
    \textit{Great Gospel}, acquired at level 64, costs 99 MP. You gain the \tstatus{Absorb} status to all elements, except \telem{Cut}, \telem{Puncture} and \telem{Crush}, until the end of the round.	

\end{multicols}

\section{Summoned Creatures}\label{sec:magic-summoned}

\begin{multicols}{2}
	
    Calls are Spells and follow the same rules as other Spells, with two exceptions: First, all Calls ignore the \tstatus{Reflect} status. Second, Calls can never be cast by Arcane Focus, Spell Weave or Critical Spell. When casting a Call, the Druid gets help from a Summoned Monster, who arises, performs the Call’s effects and disappear from of the battlefield. Nevertheless, the Druid uses his own Stats, not the beast’s, to cause effects, including damage and rolls to hit. When using the \taction{Summon} action, the Druid gains the \tstatus{Wall} status, casts the creature’s Call effect (Basic or Greater) and gain additional effects based on the creature.

    A Summoner may only have the support of the Summoned Monster if the creature itself accepted this agreement. The GM must, according to the setting, decide which Summoned Monsters exist, what the Summoner must do to bond himself with a creature, what are its effects and what are the deeds the creature will require to lend its power to a Summoner. In the following pages there will be a brief description of some of the recurring Summoned Monsters in the series.
    
    \textbf{Asura} is a humanoid creature that has three faces and six arms. Her body is female, but she has male and female faces. She uses Indian-themed clothes.
    
	\textit{Basic Call}: Minimum level: \ordinalnum{14}. MP Cost:\ 22. Roll 1d10. On a result 1, 2 or 3, grant the \tstatus{Strengthen (Mental)} status. On a result 4, 5 or 6, grant the \tstatus{Strengthen (Armor)} status. On a result 7, 8, 9 or 10, grant the \tstatus{Float} status. All status targets a group and last until the end of the next round.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{34}.\ MP Cost: 45. Roll 1d10. On a result 1, 2 or 3, grant the \tstatus{Shell} status. On a result 4, 5 or 6, grant the \tstatus{Protect} status. On a result 7 or 8, grant the \tstatus{Strengthen (Physical)} status. On a result 9 or 10, grant the \tstatus{Strengthen (Magic)} status. All status targets a group and last until the end of the next round.
    
    \textit{Summon}: Gain the \tstatus{Float} status until the end of the round.
	
    \textbf{Chocobo} is a recurring two-legged bird in the series that is often used as mounts. When summoned, it attacks with its beak. Rarely, the Summoner may summon a huge version of the creature, known as Fat Chocobo.

    \textit{Basic Call}: Minimum Level: \ordinalnum{14}.\ MP Cost: 15. Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level \telem{Puncture}-elemental magical damage to a target. In case of critical hit, you summon instead the Fat Chocobo, dealing 8 x Fire level \telem{Crush}-elemental damage to a group.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{34}.\ MP Cost: 45. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Puncture}-elemental magical damage to a target. In case of critical hit, you summon instead the Fat Chocobo, dealing 12 x Fire level \telem{Crush}-elemental damage to a group.
    
	\textit{Summon}: It has no extra effect with \taction{Summon}.
    
    \textbf{Fenrir} is a gigantic wolf, usually associated with the moon.

	\textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost:\ 24. You and your allies gain the \tstatus{Strengthen (Speed)} status over the next two rounds.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 40. You and your allies gain the \tstatus{Blink} status until the end of next round.
    
    \textit{Summon}: Gain the \tstatus{Strengthen (Mental)} status until the end of the round.

    \textbf{Ifrit} is a humanoid demon with human and goat traits, including hooves and horns. It has dominion over fire and uses it in his attacks.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 20. Roll Fire vs Water, difficulty 0. If successful, deal 7 x Fire level \telem{Fire}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 50. Roll Fire vs Water, difficulty 0. If successful, deal 10 x Fire level \telem{Fire}-elemental magical damage to a group.
    
	\textit{Summon}: Gain the \telem{Fire} \tstatus{Immune}, \telem{Shadow} \tstatus{Resist} and \telem{Ice} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Lakshmi} is a young woman with dark skin and blue robes, crowned with sun rays made by the purest gold, with the grace and dignity of a queen.

    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 25. Roll Fire vs Water, difficulty 0. On success, heal 7 x Fire level HP to a group.
    
	\textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 56. Roll Fire vs Water, difficulty 0. On success, heal 10 x Fire level HP to a group.

    \textit{Summon}: Gain the \telem{Light} \tstatus{Resist} status until the end of the round.

    \textbf{Ramuh} is a giant with a long beard and long white hair, wearing robes. He brandishes a staff and controls lightning.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 20. Roll Fire vs Water, difficulty 0. If successful, deal 7 x Fire level \telem{Lightning}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 50. Roll Fire vs Water, difficulty 0. If successful, deal 10 x Fire level \telem{Lightning}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Lightning} \tstatus{Immune}, \telem{Light} \tstatus{Resist} and \telem{Water} \tstatus{Vulnerable} status effects until the end of the round.
    
	\textbf{Shiva} is a humanoid fairy, with blue skin and elf features. She has dominion over ice.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 20. Roll Fire vs Water, difficulty 0. If successful, deal 7 x Fire level \telem{Ice}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 50. Roll Fire vs Water, difficulty 0. If successful, deal 10 x Fire level \telem{Ice}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Ice} \tstatus{Immune}, \telem{Water} \tstatus{Resist} and \telem{Fire} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Siren} is a mermaid who uses her magical songs to muddle your opponents.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 35. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Confuse} status on a target until the end of the next round.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 60. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Confuse} status on each character in a group until the end of the next round.
    
    \textit{Summon}: Until the end of the round, you are immune to all \tstatus{Mental}-type negative status.
    
    \textbf{Valefor} is a huge bird with rainbow-colored feathers.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{14} MP Cost: 20. Roll Fire vs Water, difficulty 0. If successful, deal 7 x Fire level \telem{Air}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{34} MP Cost: 60. You and up to three allies gain the \tstatus{Flight} status. At each affected character’s next action, the character descends on a target, discards the initiative die and unleashes a weapon attack dealing twice weapon physical damage. After this attack, the character loses the \tstatus{Flight} status.
    
    \textit{Summon}: Gain the conditions \tstatus{Flight} and \telem{Earth} \tstatus{Vulnerable} until the end of the round. 
    
    \textbf{Atomos} is a huge creature that looks like a giant mouth made of pink, pulsating flesh. Inside the mouth, a terrifying darkness seems to suck all the light around, as an insane vacuum or a portal to horrors beyond imagination.
    
    \textit{Basic Call}: Minimum level: \ordinalnum{24} MP Cost: 33. Roll Fire vs Water, difficulty 40. If successful, each character in a group loses 25\% of its current HP. This counts as a \tstatus{Gravity} status.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{54} MP Cost: 100. Roll Fire vs Water, difficulty 70. If successful, each character in a group loses 75\% of its current HP. This counts as a \tstatus{Gravity} status.
    
    \textit{Summon}: Until the end of the round, you are immune to all \tstatus{Fatal}-type negative status.
    
    \textbf{Carbuncle} is a small and shiny mouse-like creature, with a skin green and blue, long ears and a large polished ruby nestled on his forehead.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 40. You and your allies gain the \tstatus{Shell} status until the end of next round.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{54} MP Cost: 112. You and your allies gain the \tstatus{Reflect} status until the end of next round.
    
    \textit{Summon}: It has no extra effect with \taction{Summon}.
    
    \textbf{Catoblepas} is a strange one-eyed creature with the body of a bull, three pairs of legs, a snake-like long neck, and a pig's head.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 25. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stone} status on a target at the end of the next round.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{54} MP Cost: 105. Roll Fire vs Water, difficulty 70. If successful, inflict the \tstatus{Stone} status on each character in a group at the end of the next round.
    
    \textit{Summon}: Until the end of the round, you are immune to all \tstatus{Transform}-type negative status.
    
    \textbf{Golem} is a huge construct, made of polished stones, who protects the group.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 40. You and your allies gain the \tstatus{Protect} status until the end of next round.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{54} MP Cost: 121. You and your allies gain the \tstatus{Wall} status until the end of next round.
    
    \textit{Summon}: Gain the \tstatus{Resist} (\telem{Cut}, \telem{Crush} and \telem{Puncture}) status until the end of the round.
    
    \textbf{Kirin} has the body of a horse, the tail of a bull, the horns of a moose and the head of a dragon. His body is white, but it has a green emerald mane in his neck, shoulders and legs.
    
    \textit{Basic Call}: Minimum level: \ordinalnum{24} MP Cost: 25. Grant the \tstatus{Regen} status to a target until the end of the next round.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{54} MP Cost: 80 You and your allies gain the \tstatus{Regen} status during this and the next two next rounds.
    
    \textit{Summon}: Until the end of the round, you are immune to all \tstatus{Seal}-type negative status.
    
   \textbf{Madeen} is a great lion humanoid with dragon wings, who shoots light rays.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 35. Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level \telem{Light}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{54} MP Cost: 110. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level \telem{Light}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Light} \tstatus{Immune}, \telem{Fire} \tstatus{Resist} and \telem{Shadow} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Sylph} is a small group of six fairies with dragonfly wings who attack together.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 40. Roll Fire vs Water, difficulty 0. If successful, deal 12 x Fire level \telem{Puncture}-elemental magical damage to a target. You and your allies heal HP equal to the damage dealt, split evenly to all hurt characters in your group.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{54} MP Cost: 120. Roll Fire vs Water, difficulty 0. If successful, deal 22 x Fire level \telem{Puncture}-elemental magical damage to a target. You and your allies heal HP equal to the damage dealt, split evenly to all hurt characters in your group.
    
    \textit{Summon}: Gain the \tstatus{Float} status until the end of the round.
    
    \textbf{Titan} is a giant, very muscular, dressed in Greek tunics, who controls the Earth element.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{24} MP Cost: 35 Roll Fire vs Water, difficulty 0. If successful, deal 8 x Fire level \telem{Earth}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{54} MP Cost: 110. Roll Fire vs Water, difficulty 0. If successful, deal 17 x Fire level \telem{Earth}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Earth} \tstatus{Immune}, \telem{Lightning} \tstatus{Resist} and \telem{Air} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Unicorn} is a majestic creature with the body of a horse and a large horn on its head.
    
    \textit{Basic Call}: Minimum level: \ordinalnum{24} MP Cost: 60. Roll Fire vs Water, difficulty 0. If successful, remove all negative status effects from a target.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{54} MP Cost: 133. Roll Fire vs Water, difficulty 0. If successful, remove all negative status effects from each character in a group.
    
    \textit{Summon}: Until the end of the round, you are immune to all \tstatus{Toxic}-type  negative status.
    
    \textbf{Alexander} is a gigantic mechanical creature, vaguely humanoid, although it does not have legs. His arms are towers that touch the ground, but don’t have hands. In place of his head, a palace sits on his broad shoulders with large lights in its highest towers.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 85. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Light}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{64} MP Cost: 140. Roll Fire vs Water, difficulty 0. If successful, deal 26 x Fire level \telem{Light}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Light} \tstatus{Absorb} and \telem{Shadow} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Bahamut} is the king of dragons, a huge platinum dragon.
    
    \textit{Basic Call}: Minimum level: \ordinalnum{44} MP Cost: 80. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{non}-elemental magical damage to a target.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{64} MP Cost: 170. Roll Fire vs Water, difficulty 0. If successful, deal 28 x Fire level \telem{non}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \tstatus{Flight status} until the end of the round.
    
    \textbf{Cerberus} is a three-headed dog, big and majestic, loyal and attentive.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 90. You gain two extra initiative die, with value equal to the current phase.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{64} MP Cost: 130. You and up to three allies each gain one extra initiative dice with a value equal to the current phase.
    
    \textit{Summon}: Gain the \tstatus{Strengthen (Magic)} status until the end of the round.
    
    \textbf{Diabolos} is a demon black as the night, with bat wings, using a boiling cauldron with evil vapors.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 90. Roll Fire vs Water, difficulty 70. If successful, roll 1d10 for each target hit. Inflict status listed below to the target until the end of next round according to its d10 roll.

    1-2: \tstatus{Immobilize}, \tstatus{Mute}, \tstatus{Poison}, \tstatus{Meltdown}.

    3-4: \tstatus{Blind}, \tstatus{Disable}, \tstatus{Poison}, \tstatus{Slow}.
    
    5-6: \tstatus{Confuse}, \tstatus{Slow}, \tstatus{Virus}, \tstatus{Toad}.
    
    7-8: \tstatus{Confuse}, \tstatus{Condemn}, \tstatus{Slow}, \tstatus{Poison}.
    
    9-0: \tstatus{Berserk}, \tstatus{Blind}, \tstatus{Poison}, \tstatus{Zombie}.
        
\textit{Greater Call}: Minimum level: \ordinalnum{64} MP Cost: 120. Roll Fire vs Water, difficulty 70 against all enemies. On success, for each enemy hit, treat as if he had suffered the effects of Diabolos’ Basic Call. Roll the d10 for each enemy hit.

\textit{Summon}: Gain the \telem{Shadow} \tstatus{Absorb} and \telem{Light} \tstatus{Vulnerable} status effects until the end of the round.
    
\textbf{Kujata} is a colossal boar. Under his fur, he hides countless eyes, countless noses, countless mouths and countless tongues. It has mastery over every element.
    
    \textit{Basic Call}: Minimum level: \ordinalnum{44} MP Cost: 90. Roll Fire vs Water, difficulty 20, three times, against a group. Deal 4 x Fire level \telem{Fire}-elemental magical damage on each target hit by the first roll. Deal 4 x Fire level \telem{Ice}-elemental magical damage on each target hit by the second roll. Deal 4 x Fire level \telem{Lightning}-elemental magical damage on each target hit by the third roll. This Spell ignores the target’s Magic Armor.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{64} MP Cost: 133. Roll Fire vs Water, difficulty 20, three times, against a group. Deal 8 x Fire level \telem{Fire}-elemental magical damage on each target hit by the first roll. Deal 8 x Fire level \telem{Ice}-elemental magical damage on each target hit by the second roll. Deal 8 x Fire level \telem{Lightning}-elemental magical damage on each target hit by the third roll. This Spell ignores the target’s Magic Armor.
    
    \textit{Summon}: Gain the \tstatus{Immune} (\telem{Fire}, \telem{Ice} and \telem{Lightning}) status until the end of the round.
    
    \textbf{Leviathan} is a gigantic sea serpent, who rules the seas. His appearance brings the smell of the sea, although he can walk on dry land if desired.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 85. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Water}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{64} MP Cost: 140. Roll Fire vs Water, difficulty 0. If successful, deal 26 x Fire level \telem{Water}-elemental magical damage to a group.
    
    \textit{Summon}: Gain the \telem{Water} \tstatus{Absorb} and \telem{Lightning} \tstatus{Vulnerable} status effects until the end of the round.
    
    \textbf{Odin} is a legendary brave warrior mounted on a six-legged horse and armed with a spear and a sword tempered by the gods.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 80. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{Puncture}-elemental physical damage to a target.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{64} MP Cost: 125. Roll Fire vs Water, difficulty 0, against a group. If successful, reduce the HP of each character hit to 0. Treat this effect as a \tstatus{Fatal}-type status.
    
    \textit{Summon}: Gain the \tstatus{Strenghten (Physical)} status until the end of the round.
    
    \textbf{Phoenix} is a bird made of flame that has power over life and death.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 95. Choose an ally with 0 HP. This ally is healed to 100\% of his maximum HP.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{64} MP Cost: 150. Roll Fire vs Water, difficulty 0. If successful, deal 20 x Fire level \telem{Fire}-elemental magical damage to a group. Additionally, you may choose an ally with 0 HP. This ally is healed to 100\% of his maximum HP.
    
    \textit{Summon}: Gain the \tstatus{Reraise} and \telem{Fire} \tstatus{Immune} status effects until the end of the round.
    
    \textbf{Sraphim} is a humanoid with six feathered wings, dressed in heavenly robes.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 89. Roll Fire vs Water, difficulty 0. On success, heal 14 x Fire level HP to a group.
    
    \textit{Greater Call}: Minimum level: \ordinalnum{64} MP Cost: 165. Roll Fire vs Water, difficulty 0. On success, heal 26 x Fire level HP to a group.
    
    \textit{Summon}: Gain the \tstatus{Regen} status until the end of the round.
    
    \telem{Zodiac} is a huge serpent with four pairs of wings, ranging from feathered, draconian and bat wings.
    
    \textit{Basic Call}: Minimum Level: \ordinalnum{44} MP Cost: 85. Roll Fire vs Water, difficulty 0. If successful, deal 14 x Fire level \telem{Shadow}-elemental magical damage to a group.
    
    \textit{Greater Call}: Minimum Level: \ordinalnum{64} MP Cost: 180. Roll Fire vs Water, trouble 0. If successful, deal 31 x Fire level \telem{Shadow}-elemental magical damage to a group.
    
    \textit{Summon}: Until the end of the round, you are immune to all negative status effects.

\begin{mog}
    \baselineskip=13pt
    Summoned Monsters are major plot points in most Final Fantasy games. Even in games where no character could actually summon them, like the original Final Fantasy, Summoned Monsters appeared to guide and help the party. \pc

    As a GM, use these Summoned Monster list as a guideline. Use the ones that do fit into your campaign setting. And do not be shy about creating your own Summoned Monsters! You don't even need to create its Call effects if there is no Summoner in the party. And if there is one, use these ones as inspiration to create yours!
\end{mog}

\end{multicols}

\section{Geomancy}\label{sec:magic-geomancy}
\input {revised/geomancy.tex}

\section{Performances}\label{sec:magic-performances}
\input {revised/performances.tex}