\begin{jobdesc}[name=sjob-squire]
    While many believe that a squire is just a knight in training, some Squires never leave this status. Forgoing formal training, they never progress beyond the basic training of another Job, relying on their innate talents and intuition to progress. Be a Squire if you want to control the battlefield using offensive actions instead of reacting. \pc%

    \textbf{Representatives}: Squire Job (FFT) \pc%
\end{jobdesc}

\begin{tabjob}
    \multicolumn{2}{p{\textwidth}}{\tability{Basic Skill}: Core Ability acquired at level 1. Choose another Secondary Job. You earn that job’s first level Core Ability. Regardless of the chosen Job, the Specialties for \textit{Basic Skill} are:} \\ \nopagebreak
    \tabjobspec{}
    \crystal{earth}{12pt} \crystal{air}{12pt} & %
    \tspec{Throw Stone}: Requires Earth and Air level 2. You gain the Ranged Quick physical action \taction{Throw Stone}. You gather a rock and throw at your opponent, making an Air vs Air, difficulty 40 attack. If you hit, you deal \telem{Crush} elemental damage equal to the level-appropriate Throwing Weapon’s damage. \\
    \crystal{level}{12pt} & %
    \tspec{Equip Axe}: Requires level 1. You may equip \tequip{Heavy Weapons} and \tequip{Heavy Weapon \& Shield}. \\
    \crystal{earth}{12pt} \crystal{air}{12pt} & %
    \tspec{Artful Dodger}: Requires Earth and Air level 5. Reduce your \taction{Dodge} action’s difficulty to 40. \\
    \crystal{water}{12pt} & %
    \tspec{Draw Out}: Requires Water level 4. After using a \textit{Spell Weave (Spell)}, you may choose to not lose the weapon. If you do, you cannot use its \textit{Spell Weave (Spell)} again this combat.  \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Accumulate}: You gain the Slow (4) Physical action \taction{Focus}. Using it, you accumulate strength for your next blows. You gain the \tstatus{Strengthen (Physical)} status until the end of the next round. You may add your Air level to your Armor and your Fire level to your Magic Armor. Specialties:} \\ \nopagebreak
    \tabjobspec{}
    \crystal{water}{12pt} & %
    \tspec{Mana Well}: Requires Water level 10. Your \taction{Focus} action grants the \tstatus{Strengthen (Magic)} status effect in addition to \tstatus{Strengthen (Physical)}. \\
    \crystal{air}{12pt} & %
    \tspec{Counter Tackle}: Requires Air level 8. Whenever an enemy tries to use the \taction{Escape} action against you, increase his difficulty by 20. \\ 
    \crystal{fire}{12pt} & %
    \tspec{Spell Evasion}: Requires Fire level 10. You may use \taction{Dodge}, \taction{Block} and \taction{Parry} to avoid Spells (but not magical attacks). If you do, increase the difficulty by 20. Spells that target your party still inflict normal effects on your allies and you can only use \taction{Block} or \taction{Parry} when equipped with the correct weapons. \\
    \crystal{fire}{12pt} & %
    \tspec{Weaponcaster}: Requires Fire level 6. Whenever you cast a Spell due to a weapon ability, you may use the weapon’s Offensive Stat, rather than the Fire Stat, to hit (but not deal damage). \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Overwhelm Defenses}: Core Ability acquired at level 35. Once per phase, when you miss a non-spell attack roll or reaction, you may increase the difficulty by 20, to a maximum of 99, to re-roll it.} \\ \nopagebreak
    \tabjobspec{}
    \crystal{fire}{12pt} & %
    \tspec{Awareness}: Requires Fire level 16. You gain the Ranged magical action \taction{Awareness}. Do a Fire vs Air, diff 0, attack against all enemies. Your acute senses detect traces of enemy presence. All enemies hit lose the \tstatus{Vanish} status effect.  \\
    \crystal{earth}{12pt} \crystal{water}{12pt} & %
    \tspec{Faith and Bravery}: Requires Earth and Water level 13. Whenever you are under the effects a Weaken status effect, gain a Strengthen status effect. \tstatus{Weaken (Armor)} gives you \tstatus{Strengthen (Physical)}. \tstatus{Weaken (Mental)} gives you \tstatus{Strengthen (Magical)}. \tstatus{Weaken (Physical)} gives you \tstatus{Strengthen (Armor)}. \tstatus{Weaken (Magical)} gives you \tstatus{Strengthen (Mental)}. \\
    \crystal{earth}{12pt} \crystal{air}{12pt} & %
    \tspec{Mighty Dodge}: Requires Air and Earth level 13. You may use the \taction{Attack} action as a free action after you succeed with \taction{Dodge}, \taction{Block} or \taction{Parry}. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Tailwind}: Core Ability acquired at level 50. You gain the Ranged Quick action \taction{Yell}. Use it on an ally. The target gains one extra initiative dice with value equal to the current phase.} \\ \nopagebreak
    \tabjobspec{}
    \crystal{air}{12pt} \crystal{water}{12pt} & %
    \tspec{Ordered Retreat}: Requires Air and Water level 16. When you succeed with the \taction{Escape} action, treat as if all allies succeeded with a \taction{Escape} action this phase. \\
    \crystal{earth}{12pt} \crystal{air}{12pt} \crystal{fire}{12pt} \crystal{water}{12pt} & %
    \tspec{Graduation}: Requires Earth, Air, Fire and Water level 12. Choose an action of any other Secondary Job.  You gain that action. This ability cannot grant reactions. \\
    \crystal{fire}{12pt} & %
    \tspec{Imbue}: Requires Fire level 18. Gain the quick magical action \taction{Imbue}. With it, you consume a battle item to give a weapon the Imbue (spell) Equipment Effect. This effect allows the charater with the equipped weapon to cast the consumed battle item's spell as an action, without spending MP\@. All abilities that effect Spell Weave affect Imbue as well. The Imbue property lasts until it is used to cast the spell or \taction{Imbue} is used again on the same weapon. \\
\end{tabjob}