A magician expert in time and cosmic magic, able to manipulate the battlefield and use spells that support its allies and hinder its enemies. Like all magicians, its main stats are Fire and Water. Its spells can change the flow of battle, but ultimately the power of the Time Mage relies not in winning the battles directly, but indirectly giving the party the tools to do so. The list of Spells and its description are in the Spells section, starting at page 70. \pc

\textbf{Representatives}: Time Mage Job (FFV, FFT, FFTA) \pc

\begin{jobstats}
    HP Bonus & 3x & 4x & 5x & 6x \\
    MP Bonus & 3x & & 4x & \\
    Armor   & \multicolumn{4}{l}{ Light } \\
    Weapons & \multicolumn{4}{l}{\begin{tabular}{@{}l} Claws / Gloves \\ Light Swords / Knives \\ Staves \\ Wands \\ \end{tabular}} \\
\end{jobstats}

\begin{ffminipage}
{\centering \textbf{Abilities}\par }

\tability{Arcane Studies}: Core Ability acquired at level 1. You can
equip light armor and the following weapons: \tequip{Claws / Gloves};
Light Swords / Knives; Staves; Wands. Your HP bonus is 3 times
your level, the multiplier increasing by 1 at levels 15, 30 and 60.
Your bonus MP is 3 times your level, the multiplier increasing by
1 at level 30. \pw

\begin{jobspec}
\crystal{level}{12pt} \crystal{fire}{12pt} & %
\tspec{Arcane Mystery: Old}: Requires Fire level 20 and character level 64. You gain the \tspell{Old} Spell. \\
\crystal{level}{12pt} \crystal{fire}{12pt} & %
\textit{Arcane Mystery: Ultima}: Requires Fire level 20 and character level 64. You gain the Ultima Spell. \\
\crystal{level}{12pt} \crystal{fire}{12pt} & %
\textit{Arcane Mystery: Doomsday}: Requires Fire level 20 and character level 64. You gain the Doomsday Spell. \\
\end{jobspec}
\end{ffminipage}

\begin{ffminipage}
\noindent\textbf{\textit{Elemental Magic}}: Core Ability acquired at level 1. You gain one Elemental Spell group: \textbf{Lightning}, \textbf{Ice}, or \textbf{Fire}. \\

\begin{jobspec}
\crystal{water}{12pt} & %
\textit{Elemental Mastery} Requires Water level 3. You gain one Elemental Spell group. After reaching level 15, gain another Elemental Spell group. \\
\crystal{earth}{12pt} & %
\textit{Elemental Burst} Requires Earth level 4. Whenever you use a Spell against a single target, you may deal 25\% of the Spell’s damage to another opponent, chosen randomly, ignoring their Magic Armor. \\
\crystal{fire}{12pt} & %
\textit{Elemental Shock} Elemental Shock: Requires Fire level 5. Whenever you deal damage with an Elemental Spell, increase all targets’ initiative dice’s values by 1, up to a maximum of 10. \\
\end{jobspec} \\
\end{ffminipage}

\begin{ffminipage}
\noindent\textbf{\textit{Transmutation}}: Core Ability acquired at level 1. You gain one Transmutation Spell group: \textbf{Death}, \textbf{Transform} or \textbf{Poison}. \\

\begin{jobspec}
\crystal{fire}{12pt} & %
\textit{Transmutation Mastery} Requires Fire level 6. You gain one Transmutation Spell group. \\
\crystal{air}{12pt} \crystal{water}{12pt} & %
\textit{Piercing Arcana} Requires Air and Water level 5. Your Spells ignore the targets’ status resistance. This has no effect on status immunities. \\
\crystal{earth}{12pt} \crystal{fire}{12pt} & %
\textit{Magic Resistance} Requires Earth and Fire level 4. You resist all status effects you are able to inflict with a Transmutation Spell. \\
\end{jobspec} \\
\end{ffminipage}

\begin{ffminipage}
\noindent\textbf{\textit{Worldly Magic}}: Core Ability acquired at level 15. You gain one Worldly Spell group: \textbf{Water}, \textbf{Earth}, or \textbf{Shadow}. \\

\begin{jobspec}
\crystal{earth}{12pt} & %
\textit{Worldly Mastery}: Requires Earth level 8. You gain one Worldly Spell group. \\
\crystal{fire}{12pt} \crystal{water}{12pt} & %
\textit{Worldly Shock}: Requires Fire level 10 and Water level 7. Your Spells ignore half of targets’ MARM. \\
\crystal{air}{12pt} \crystal{water}{12pt} & %
\textit{Careful Casting}: Requires Air level 5 and Water level 8. You may, as you cast a Spell, make it a Slow (3) action. Doing so will reduce by 30 its difficulty, to a minimum of zero. All difficulties listed in the Spell are reduced by this effect. \\
\end{jobspec}
\end{ffminipage}

\begin{ffminipage}
\noindent\textbf{\textit{Magical Expert}}: Core Skill acquired at level 30. You gain one Expert Spell group: \textbf{Drain}, \textbf{Hex}, or \textbf{Mage Bane}. \\

\begin{jobspec}
\crystal{earth}{12pt} \crystal{air}{12pt} \crystal{water}{12pt} & %
\textit{Multi-Expert}: Requires Earth, Air and Water level 7. You gain one Expert Spell group. \\
\crystal{fire}{12pt} & %
\textit{Obliterate}: Requires Fire level 12. When you use an Expert Spell, before applying the Spell’s effects, if the target has the Protect, Shell, and/or Reflect statuses they cease to affect him until the end of the round. \\
\crystal{air}{12pt} \crystal{fire}{12pt} & %
\textit{Favored Element}: Requires Air level 9 and Fire level 10. Choose an element. Your attacks of the chosen element ignore the target’s elemental resistance and deal 50\% damage to immune targets. \\
\end{jobspec}
\end{ffminipage}