\begin{jobdesc}[name=pjob-warrior]
  A focused fighter in heavy armor, specialist in melee combat. Its main stats are Earth and Air, with Water as tertiary stat. Regardless of the Stat you focus, Warriors may work offensively or defensively; they can either focus on causing as much damage as possible or on protecting the group to by weakening their opponent. Regardless of the chosen skills, it is a simple class to play: buy the best possible equipment, and you will have enough HP, damage and defenses to defeat any opponent.

  \textbf{Representatives}: Dragoon Job (FFIII, FFV, FFXI, FFT, FFTA), Uhlan Job (FFXIIZJ), Kain Highwind (FFIV), Cid Highwind (FFVII), Ward Zabac (FFVIII), Freya Crescent (FFIX), Gladiator Job (FFTA), Fighter Job (FFI, FFIII), Warrior Job (FFXI), Adelbert Steiner (FFIX), Auron (FFX), Knight Job (FFIII, FFV, FFT), Leo Cristophe (FFVI), Soldier Job (FFTA), Cyan Garamonde (FFVI), Cloud Strife (FFVII), Squall Leonhart (FFVIII), Tidus (FFX)



\end{jobdesc}

\begin{ffminipage}
  {\centering \textbf{Abilities} \par{}}

  Master of Arms: Core Ability acquired at level 1. You can equip heavy armor and the following weapons: Light Sword/ Knives; Claws / Gloves; Heavy Weapon \& Shield; Heavy Weapon; Katana; and Polearms. Your HP bonus is 5 times your level, the multiplier increasing by 1 at levels 15, 30 and 60. Your MP bonus is zero, and increases by 1 times your level at level 30.

  \begin{jobchoice}
    Arc: Requires Fire level 3. You gain Quick action !Arc. This action allows you to launch a wave of Chi energy against your target and carry out an attack with your weapon causing all the equipment effects normally and to adding Ranged to the attack.

    Pommel Strike: Requires Earth level 3. You gain the Quick action !Pommel Strike. You attack your opponent with your weapon’s hilt at a time and place where he doesn’t expect. Do an attack roll with your weapon, causing half of your weapon’s physical damage. If the target is preparing a Slow action, he loses it.

    Dirty Fighting: Requires Air level 3. You gain Quick action !Dirty Fighting. You throw sand in the eyes of the opponent, attack their genitals or distract them in any way. Do an attack roll with your weapon, causing normal physical damage. Unlike other attacks, do not add the 1’s digit to damage. If the target suffers at least 1 damage, he cannot do Reactions this phase.
  \end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
  Power Attack: Core Ability acquired at level 1. You earn one of the three Power Attack actions below:

  \begin{jobchoice}[header=false]
    !Jump is a Quick action. Using it, you jump an incredible height and gain the Flight status. In your next action, you dive on a target, discarding the initiative die and attacking with your weapon. If you hit, inflict twice weapon damage. After the attack, you lose the Flight status.

    !Mighty Strike is a Quick action. Attacking with all your might, without preparation or any worry about accuracy, you deliver a devastating attack. Perform an attack with your weapon but increasing the difficulty by 30. Your attack does twice weapon damage, plus all the equipment effects as usual.

    !Lunge is also a Quick action. You unleash an attack with your weapon, ignoring your defense to cause as much damage as possible. You inflict twice weapon damage, but over the next 10 phases, lower by 30 points the difficulty of any attack aimed at you. You can’t use this action again until this effect ends.
  \end{jobchoice}

  \begin{jobchoice}
    Dragon Horn: Requires Earth and Air level 12. After using a Power Attack, you can discard any number of initiative dice, regardless of their value, to immediately repeat the attack, once per discarded die, against the same target. With !Jump, the attacks happen before the character lose the Flight status. With !Lunge, add the number of phases with decreased difficulty. For example, if Dragon Horn is used to !Lunge three times, you suffer its effects for the next 30 phases.

    Quadra Slam: Requires Earth level 10 and Water level 8. You gain the Slow (4) action !Quadra Slam. When using it, you move with incredible speed, striking four consecutive attacks with your weapon with just one action. These attacks target random enemies and cause half weapon damage each, ignoring the target’s Armor.

    Adroit: Requires Earth and Air level 7. Whenever you use a Warrior ability other than a weapon attack, you can choose to use either Earth or Air as Offensive Stat.
  \end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
  Feign Weakness: Core Ability acquired at level 15. You gain the Slow(1) physical action !Life Break. When using it, focus your chi energy to perform an Earth vs Earth attack, difficulty 40, against a target. If successful, this action causes Cut-elemental damage equal to (your max HP - your current HP). Don’t add the singles digit to damage. This action ignores the Strengthen (Physical) status and may not deal over 999 damage.

  \begin{jobchoice}
    Power Break: Requires Earth level 8 and Air level 10. You gain the Quick physical action !Power Break, which is an attack that weakens the muscle power of the target. Perform an Earth vs Air attack, difficulty 70. If successful, the target receives the Weaken (Physical) status until the end of the next round.

    Magic Break: Requires Earth level 8 and Water level 10. You gain the Quick physical action !Magic Break, which is an attack that weakens the magical power of the target. Perform an Air vs Fire attack, difficulty 70. If successful, the target receives the Weaken (Magic) status until the end of the next round.

    Armor Break: Requires Earth level 10 and Air level 8. You gain the Quick physical action !Armor Break, which is an attack that weakens the resistance of the target. Perform an Air vs Earth attack, difficulty 70. If successful, the target receives the Weaken (Armor) status until the end of the next round.

    Mental Break: Requires Earth level 8 and Fire level 10. You gain the Quick physical action !Mental Break, which is an attack that weakens the magic resistance of the target. Perform an Earth vs Water attack, difficulty 70. If successful, the target receives the Weaken (Mental) status until the end of the next round.
  \end{jobchoice}
\end{ffminipage}


\begin{ffminipage}
  Cleave: Core Ability acquired at level 24. You gain a cleaving action, which can be one of the two below:

  \begin{jobchoice}[header=false]
    !Slash-All is a Slow (2) action. Moving with speed, you can unleash an attack with your weapon against up to three targets. Each target takes damage equal to 75\% of your weapon damage, plus all the equipment effects.

    !Blade Beam is also a Slow (2) action. You shoot a wave of chi energy at a target, performing an attack with your weapon that causes normal damage. If it succeeds, you can repeat the attack against two other targets, but these secondary attacks ignore the target’s Armor and cause 50\% of the damage dealt to the first target, after reducing by the first target’s Armor. All these attacks are Ranged, regardless of the equipped weapon.
  \end{jobchoice}

  \begin{jobchoice}
    Powerful Cleave: Requires Air and Water level 10. Your cleaving action deal 100\% weapon damage to all targets instead of the reduced damage.

    Wide Cleave: Requires Air and Fire level 10. !Slash-All can target any number of enemies instead of three. The secondary attacks of the !Blade Beam action can target any number of enemies besides the first target.

    Mastery of Destruction: Requires Fire and Water level 10. Your !Power Break, !Magic Break, !Armor Break and !Mental Break actions may target up to three enemies instead of only one. This Specialty does not give access to any extra actions, only modifies the actions that you own.
  \end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
  Dragon Breath: Core Ability acquired at level 42. You gain the Slow (3) physical action !Dragon Breath. This action allows you to use the weakness of your enemy against itself. If you have success in an Air vs Air attack, difficulty 40, the target is dealt Crush- elemental damage equal to (target’s max HP – target’s current HP). Don’t add the singles digit to damage. This action ignores the Strengthen (Physical) status and may not deal over 999 damage.

  \begin{jobchoice}
    Lethal Blow: Requires Earth level 16. When using !Dragon Breath, reduce the target's Armor before applying 999 damage limit, instead of after.

    Double Cut: Requires Air and Water level 12. You gain the Slow (2) action !Double Cut. With it, do two attacks with your weapon in quick succession at the target, dealing weapon damage and effects. This ability may achieve critical hits, causing double damage.

    Martial Versatility: Requires Earth level 11 and Air, Fire and Water level 9. You gain one of the following Specialties: Power Break, Magic Break, Armor Break or Mental Break, even if you haven’t met the requirements and even if you already chose another Specialty to the Feign Weakness ability.
  \end{jobchoice}
\end{ffminipage}

\begin{ffminipage}
  Unwavering Courage: Core Ability acquired at level 60. You become immune to Weaken (Physical), Weaken (Magic), Weaken (Armor), Weaken (Mental) and Weaken (Speed).

  \begin{jobchoice}
    Finishing Touch: Requires Air level 20. You gain the Slow (5) action !Finishing Touch. Make two weapon attacks, difficulty 70, against the target. If both attacks are successful, inflict the Stone status. If the target is immune to Stone or if only one attack is successful, you deal double weapon damage. If the enemy is not immune to Fatal-type statuses and one or both blows land a critical hit, reduce your opponent to 0 HP. Treat this last effect as a Fatal type status.

    Shock: Requires Fire level 20. You gain the Ranged Slow (5) physical action !Shock. This action releases a burst of Chi that affects all your enemies. Perform an Earth vs Fire attack, difficulty 40. Each affected opponent suffers twice your weapon damage.

    Iaijutsu: Requires Water level 20. You gain the Slow (4) physical action !Cleave. You go through your opponents with a sharp blow. Make an Air vs Earth attack, difficulty 70, against all your enemies. Instantly reduce to 0 HP all affected opponents. This effect counts as a Fatal type status.
  \end{jobchoice}
\end{ffminipage}