\begin{jobdesc}[name=pjob-whitemage]
    A magician skilled in healing and protection magic, master of the beneficial magical energies. Its main stats are Water and Fire, with Earth as tertiary stat. Your Spells are primarily defensive in nature, giving you few tools to deal directly with your enemies. The list of Spells and their description is in the~\nameref{sec:magic-white}~section, starting at page~\pageref{sec:magic-white}. \pc%

    \textbf{Representatives}: Porom (FFIV), Rosa Farrell (FFIV), White Mage Job (FFI, FFIII, FFV, FFX-2, FFXI, FFT, FFTA) \pc%

    \jobstats[hpa=3x,hpb=4x,hpc=5x,hpd=6x,mpa=2x,mpb=3x,mpc=4x,armor=Light,weapons=Claws / Gloves \\ Staves \\ Wands]
\end{jobdesc}

\begin{tabjob}
    \multicolumn{2}{p{\textwidth}}{\tability{Arcane Devotion}: Core Ability acquired at level 1. You are a white mage, and gain the \tspellgroup{Healing} Spell Group and the multipliers and equipment choices above.} \\
    \tabjobspec{}
        \crystal{level}{12pt} \crystal{fire}{12pt} & %
        \tspec{Arcane Mystery: Holy}: Requires Fire level 20 and character level 64. You gain the \tspell{Holy} Spell. \\
        \crystal{level}{12pt} \crystal{fire}{12pt} & %
        \tspec{Arcane Mystery: Rebirth}:  Requires Fire level 20 and character level 64. You gain the \tspell{Rebirth} Spell. \\
        \crystal{level}{12pt} \crystal{fire}{12pt} & %
        \tspec{Arcane Mystery: Shield}: Requires Fire level 20 and character level 64. You gain the \tspell{Shield} Spell. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Heavenly Magic}: Core Ability acquired at level 1. You gain one Heavenly Spell group: \tspellgroup{Light}, \tspellgroup{Air}, or \tspellgroup{Purify}.} \\
    \tabjobspec{}
        \crystal{air}{12pt} & %
        \tspec{Heavenly Mastery}: Requires Air level 3. You gain one Heavenly Spell group. \\
        \crystal{fire}{12pt} \crystal{water}{12pt} & %
        \tspec{Heavenly Blessing}: Requires Fire level 3 and Water level 5. You may target two characters with a single target Heavenly or Protective Spell if you spend twice the MP cost. \\
        \crystal{earth}{12pt} & %
        \tspec{Heavenly Warrior} Requires Earth level 3. You can equip \tequip{medium armor} and the weapon \tequip{Weapons \& Shields}. Increase your HP bonus multiplier at all levels by 1 if its level 1 value is 4x or lower. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Protective Magic}: Core Ability acquired at level 15. You gain one Protective Spell group: \tspellgroup{Elemental}, \tspellgroup{Life}, \tspellgroup{Armor}, \tspellgroup{Shield}, or \tspellgroup{Images}.} \\
    \tabjobspec{}
        \crystal{earth}{12pt} & %
        \tspec{Protective Mastery}: Requires Earth level 7. You gain one Protective Spell group. \\
        \crystal{air}{12pt} \crystal{fire}{12pt} & %
        \tspec{Magic Shield}: Requires Air level 8 and Fire level 5. You can use Protective spells on yourself as a Reaction when an enemy targets you with an action. Spells cast as Reaction end its effects at the end of the round and can't target other characters. \\
        \crystal{earth}{12pt} \crystal{water}{12pt} & %
        \tspec{Mana Armor}: Requires Earth and Water level 8. As a free action at the beginning of each round, you can erect a magical shield on yourself that lasts one round. Whenever you take damage with this shield on, you lose MP instead of HP\@. If your MP is zero, you lose HP as normal. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Versatile Protection}: Core Ability acquired at level 15. You gain another Protective Spell Group: \tspellgroup{Elemental}, \tspellgroup{Life}, \tspellgroup{Armor}, \tspellgroup{Shield}, or \tspellgroup{Images}.} \\
    \tabjobspec{}
        \crystal{fire}{12pt} & %
        \tspec{Deep Studies}: Requires Fire level 15. You gain one Heavenly, Protective or Psychic Spell group. \\
        \crystal{earth}{12pt} \crystal{air}{12pt} & %
        \tspec{Martial Dabbler}: Requires Earth and Air level 8. Choose a weapon type other than \tequip{Instruments} and \tequip{Twin Blades}. You may equip weapons of that type. \\
        \crystal{air}{12pt} \crystal{fire}{12pt} & %
        \tspec{Offensive Barriers}: Requires Air level 10 and Fire level 9. Whenever you cast an \tspellgroup{Elemental}, \tspellgroup{Armor}, \tspellgroup{Shield}, or \tspellgroup{Images} spell, you may do it offensively. If you do, increase the Spell's difficulty to 70. Instead of granting a status effect, an offensively cast spell removes the status effect from the target. An offensive \tspell{Shell} Spell, for example, removes the \tstatus{Shell} status from the target. This Ability can't remove permanent status effects. \\
    \tabjobsep%
    \multicolumn{2}{p{\textwidth}}{\tability{Psychic Magic}: Core Ability acquired at level 30. You gain one Psychic Spell group: \tspellgroup{Madness}, \tspellgroup{Enchantment}, or \tspellgroup{Vulnerability}.} \\
    \tabjobspec{}
        \crystal{fire}{12pt} \crystal{water}{12pt} & %
        \tspec{Psychic}: Requires Fire and Water level 11. You gain one Psychic Spell group. \\
        \crystal{earth}{12pt} \crystal{air}{12pt} & %
        \tspec{Asceticism}: Requires Earth level 8 and Air level 10. Even if you have the \tstatus{Stone}, \tstatus{Berserk} and/or \tstatus{Stop} statuses, you can act normally if your action removes the status. \\
        \crystal{earth}{12pt} \crystal{fire}{12pt} & %
        \tspec{Elemental Blessing}: Requires level 8 in Earth and 12 in Fire. Choose an element. You gain the \tstatus{Resist} status for that element permanently. \\
\end{tabjob}